---
title: "Lab Reports"
description: |
  Reporting used to track Lab Monitoring
output:
  html_document:
    toc: true
    theme: cerulean
date: '`r Sys.time()`'
---

Notes:

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT
- Please reach out to atediarjo@gmail.com for bug reports

Description:

This report is used to monitor data collection for Lab coming from Efficacy and PK. Design specs are based on this [Reporting Document](https://docs.google.com/document/d/1Q9t3Mkul3hmppxfgbhOXzkaDPAf_iuotiE5ruooY7AM/edit)

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tidyr)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
```

```{r}
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}
```

```{r}
#################################
# Fetch v0 demography
#################################
# pk <- cloudbrewr::aws_s3_get_table(
#   bucket = 'databrew.org',
#   key = 'kwale/clean-form/pk/pk.csv'
# ) %>%
#   pad_hhid()

efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/efficacy/efficacy.csv'
) %>%
  pad_hhid()


lab <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/lab/lab.csv'
) %>%
  pad_hhid()

lab2 <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/lab2/lab2.csv'
) %>%
  pad_hhid()

lab_metadata_zp <- cloudbrewr::aws_s3_get_object(
  bucket = 'databrew.org',
  key = 'metadata/lab_metadata.zip'
) 


lab_ovr <- 
    bind_rows(
        lab %>% 
            mutate(
              extid = as.character(extid),
              dob = as.character(dob),
              sample = as.character(sample),
              visit = as.character(visit),
              sample_status = as.character(sample_status),
              start_time = lubridate::as_datetime(start_time),
              efficacy_reason = as.character(efficacy_reason),
              pk_reason = as.character(pk_reason),
              study = as.character(study),
              incidences = ifelse(!is.na(match_tracking_incidence_select),
                                       match_tracking_incidence_select,
                                       ifelse(!is.na(match_tracking_incidence_select2),
                                              match_tracking_incidence_select2,
                                              NA)),
               date_sample = lubridate::date(date_sample), 
               cl_sample = as.character(cl_sample), 
               pkid = as.character(pkid), 
               pk_sample_number = as.character(pk_sample_number), 
               icf_status_efficacy = as.character(icf_status_efficacy),
               icf_status_safety_adult = as.character(icf_status_safety_adult),
               icf_status_pk = as.character(icf_status_pk)
              
            ) %>%
            dplyr::select(
              extid,
              sample, 
              dob,
              visit,
                          sample_status, 
                          start_time, 
                          efficacy_reason,
                          pk_reason, 
                          incidences,
                          study,
                          date_sample, 
                          cl_sample, 
                          pkid, 
                          pk_sample_number, 
                          icf_status_efficacy,
                          icf_status_safety = icf_status_safety_adult,
                          icf_status_pk),
        lab2 %>%
            mutate(
              extid = as.character(extid),
              dob = as.character(dob),
              sample = as.character(sample),
              visit = as.character(visit),
              sample_status = as.character(sample_status),
              start_time = lubridate::as_datetime(start_time),
              efficacy_reason = as.character(efficacy_reason),
              pk_reason = as.character(pk_reason),
              study = as.character(study),
              incidences = as.character(incidences),
              date_sample = lubridate::date(date_sample), 
              cl_sample = as.character(cl_sample), 
              pkid = as.character(pkid), 
              pk_sample_number = as.character(pk_sample_number), 
              icf_status_efficacy = as.character(icf_status_efficacy),
              icf_status_safety = as.character(icf_status_safety),
              icf_status_pk = as.character(icf_status_pk)
            ) %>%
            dplyr::select(
              extid,
              sample, 
              dob,
              visit,
                          sample_status, 
                          start_time, 
                          efficacy_reason,
                          pk_reason, 
                          incidences,
                          study,
                          date_sample, 
                          cl_sample, 
                          pkid, 
                          pk_sample_number, 
                          icf_status_efficacy,
                          icf_status_safety,
                          icf_status_pk)
    ) %>%
    mutate(quarantine_reasons = ifelse(!is.na(efficacy_reason),
                                       efficacy_reason,
                                       ifelse(!is.na(pk_reason),
                                              pk_reason, NA))) %>%
    dplyr::select(-efficacy_reason, -pk_reason) %>%
    arrange(desc(start_time)) %>%
    dplyr::distinct(sample, .keep_all = TRUE)  %>%
    dplyr::mutate(dob = stringr::str_remove(dob, ".")) %>% 
    dplyr::mutate(age = as.numeric((lubridate::date(start_time) - lubridate::date(dob))/365.25))%>%
    dplyr::select(-start_time)

unzip(lab_metadata_zp$file_path, exdir = '/tmp')

lab_metadata <- fread('/tmp/lab_metadata/lab_data.csv') %>%
    dplyr::mutate(dob = stringr::str_remove(dob, ".")) %>% 
    dplyr::mutate(age_new = as.numeric((lubridate::date(start_time) - lubridate::date(dob))/365.25)) 

```

### a. Lab Summary Table

```{r}
report_list <- list()
report_list$eff <- lab_metadata %>% 
    dplyr::filter(study == 'efficacy' | study == 'pk') %>% 
    dplyr::group_by(study) %>% 
    dplyr::summarise(val = n_distinct(sample)) %>% 
    dplyr::mutate(metric = 'Samples collected to date (field)')

report_list$smpl_all <- lab_ovr %>%
    dplyr::filter(!is.na(sample_status)) %>%
    dplyr::group_by(study) %>% 
    dplyr::summarise(val = n_distinct(sample)) %>% 
    dplyr::ungroup() %>%
    dplyr::mutate(metric = glue::glue('Samples logged in Lab')) %>% 
    dplyr::select(study, metric, val)


report_list$smpl_need_logging <- report_list$eff %>% 
    dplyr::inner_join(report_list$smpl_all, by = 'study') %>% 
    dplyr::mutate(val = val.x - val.y,
                  metric = 'Samples to be logged in Lab') %>% 
    dplyr::select(study, metric, val)


report_list$smpl_by_status <- lab_ovr %>%
    dplyr::filter(!is.na(sample_status)) %>%
    dplyr::group_by(study, sample_status) %>% 
    dplyr::summarise(val = n_distinct(sample)) %>% 
    dplyr::ungroup() %>%
    dplyr::mutate(metric = glue::glue('Samples {sample_status}'),
                  study = 'efficacy') %>% 
    dplyr::select(study, metric, val)


d <- report_list %>%
    purrr::reduce(dplyr::bind_rows) %>% 
    dplyr::select(study, metric, val) %>% 
    tidyr::pivot_wider(id_cols = metric,
                       names_from = study, 
                       values_from = val)

reactable(d)
```

### b. Field Efficacy & PK Samples

```{r}
d <- lab_metadata %>% 
    dplyr::filter(!sample %in% lab_ovr$sample) %>%
  tibble::as_tibble() %>%
  dplyr::select(extid, 
                `barcode` = sample, 
                study, 
                age, 
                visit,
                `date` = date_sample, 
                `CL` = cl_sample, 
                `PK ID` = pkid,
                `PK Sample Number` = pk_sample_number,
                `ICF Status Efficacy` = icf_status_efficacy,
                `ICF Status Safety` = icf_status_safety,
                `ICF Status PK` = icf_status_pk,
                `Sample Status` = sample_status) %>% 
  dplyr::filter(is.na(`Sample Status`))



element_id <- "field_interactive_tbl"
tbl <- reactable(d, 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'field_interactive_tbl.csv')
```


### c. Approved/Quarantined/Pending samples Efficacy & PK Interactive table 

```{r}
d <- lab_ovr %>% 
  tibble::as_tibble() %>%
  dplyr::select(extid, 
                `barcode` = sample, 
                study, 
                age, 
                visit,
                `date` = date_sample, 
                `CL` = cl_sample, 
                `PK ID` = pkid,
                `PK Sample Number` = pk_sample_number,
                `ICF Status Efficacy` = icf_status_efficacy,
                `ICF Status Safety` = icf_status_safety,
                `ICF Status PK` = icf_status_pk,
                `Sample Status` = sample_status,
                `Incidences` = incidences) %>% 
  dplyr::filter(!is.na(`Sample Status`))


element_id <- "lab_interactive_tbl"
tbl <- reactable(d, 
    columns = list(
      age = colDef(format = colFormat(digits = 2))
    ), 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'lab_interactive_tbl.csv')
```
