---
title: "Pharmacy Reports"
description: |
  Reporting used to track Pharmacy, Pharmacy SFA, Pharmacy FA and Field CLs
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

Notes:

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT
- Please reach out to atediarjo@gmail.com for bug reports

Description:

This report is used for Pharmacy based on this [Reporting Document](https://docs.google.com/document/d/15-BOyB24J81B7JwMggHYBmX8RGpoC4raIKk8TOkdrf0/edit#heading=h.vk0h181v4mre)

Several notations are used here:

- `alb`: Albendazole
- `ivm`: Ivermectin
- `coartem20`: Coartem 20/120 mg
- `coartem80`: Coartem 80/480 mg
- `prdt`: Pregnancy Test Kits

Disclaimer: 

Only `safety`, `safetynew` is used for CL reporting. Thus there is only ALB being reported from site.


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tidyr)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
```

```{r}
INPUT_KEY <- list(
  sepk_icf_verification = glue::glue('{SE_FOLDER_TARGET}/sepk_icf_verification/sepk_icf_verification.csv'),
  sepk_icf_resolution =  glue::glue('{SE_FOLDER_TARGET}/sepk_icf_resolution/sepk_icf_resolution.csv'),
  safety = glue::glue('{SE_FOLDER_TARGET}/safety/safety.csv'),
  safetynew = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew.csv'),
  efficacy =  glue::glue('{SE_FOLDER_TARGET}/efficacy/efficacy.csv'),
  pkday0 =  glue::glue('{SE_FOLDER_TARGET}/pkday0/pkday0.csv')
)


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}
```


```{r}
#################################
# Fetch v0 demography
#################################
pharmacy_fa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_fa/pharmacy_fa.csv'
) %>%
  pad_hhid()
pharmacy_sfa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_sfa/pharmacy_sfa.csv'
) %>%
  pad_hhid() 
pharmacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy/pharmacy.csv'
) %>%
  pad_hhid() 

v0_repeat <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv'
) %>%
  pad_hhid() 


efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/efficacy/efficacy.csv')) %>%
  pad_hhid()

safety <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety.csv')) %>%
  pad_hhid()

safetynew <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew.csv')) %>%
  pad_hhid()

safety_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety-repeat_individual.csv')) %>%
  pad_hhid()

safetynew_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew-repeat_individual.csv')) %>%
  pad_hhid()


assignment <- cloudbrewr::aws_s3_get_table(
  bucket = 'bohemia-lake-db',
  key = glue::glue('bohemia_prod/dim_arm_assignment/assignments.csv')) %>%
  pad_hhid()
```


```{r}

## pharmacy
pharmacy_list <- list()

# pharmacy initial stock
pharmacy_list$pharmacy_initial_stock <- pharmacy %>% 
    dplyr::filter(source_entry == 'supplier') %>% 
    dplyr::select(alb_tabno, 
                  ivm_tabno, 
                  coartem80_tabno, 
                  coartem20_tabno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_arrival = sum(value)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt'))


pharmacy_list$pharmacy_sent_to_sfa <- pharmacy %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(alb_tabno, 
                  ivm_tabno, 
                  coartem80_tabno, 
                  coartem20_tabno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_dispatch = sum(value)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt'))

pharmacy_list$pharmacy_sent_back_form_sfa <- pharmacy %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'field') %>% 
    dplyr::select(starts_with('unused'),
                  unusable_coartem24_no) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>%
    dplyr::summarise(pharmacy_return = sum(value)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt'))

pharmacy_flow_df <- pharmacy_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )


## pharmacy
pharmacy_sfa_list <- list()

# pharmacy initial stock
pharmacy_sfa_list$pharmacy_sfa_initial_stock <- pharmacy_sfa %>% 
    dplyr::filter(source_entry == 'pharmacy') %>% 
    dplyr::select(alb_tabsno, 
                  ivm_tabletno, 
                  coartem80_tabletno, 
                  coartem24_tabletno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_sfa_arrival = sum(value))


pharmacy_sfa_list$pharmacy_sfa_sent_to_fa <- pharmacy_sfa %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(alb_tabsno, 
                  ivm_tabletno, 
                  coartem80_tabletno, 
                  coartem24_tabletno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_sfa_dispatch = sum(value))


pharmacy_sfa_list$return <- pharmacy_sfa %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'fa') %>% 
    dplyr::select(starts_with('unused'),
                  unusable_coartem24_no) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_sfa_return = sum(value))

pharmacy_sfa_flow_df <- pharmacy_sfa_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )



## pharmacy
pharmacy_fa_list <- list()

# pharmacy initial stock
pharmacy_fa_list$initial_stock <- pharmacy_fa %>% 
    dplyr::filter(source_entry == 'sfa') %>% 
    dplyr::select(alb_tabletno, 
                  ivm_tabletno, 
                  coartem80_tabletno, 
                  coartem24_tabletno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_fa_arrival = sum(value)) 


pharmacy_fa_list$dispatch <- pharmacy_fa %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(alb_tabletno, 
                  ivm_tabletno, 
                  coartem80_tabletno, 
                  coartem24_tabletno,
                  prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_fa_dispatch = sum(value))

pharmacy_fa_list$return <- pharmacy_fa %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'cl') %>% 
    dplyr::select(starts_with('unused'),
                  unusable_coartem24_no) %>%
    tidyr::pivot_longer(cols =  everything()) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    tidyr::drop_na() %>% 
    dplyr::group_by(name) %>% 
    dplyr::summarise(pharmacy_fa_return = sum(value))


pharmacy_fa_flow_df <- pharmacy_fa_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )



cl_list <- list()
cl_list$safety <- safety_repeat_individual %>% 
    dplyr::select(num_ivermectin_tablets_taken,
                  num_ivermectin_tablets_taken_2,
                  num_albendzole_pills,
                  num_albendzole_pills_2,
                  num_extra_albendazole,
                  num_extra_albendazole_2,
                  num_extra_ivermectin,
                  num_extra_ivermectin_2,
                  preg_test_result, 
                  preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = everything()) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::group_by(grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(value))


cl_list$safetynew <- safetynew_repeat_individual %>% 
    dplyr::select(num_ivermectin_tablets_taken,
                  num_ivermectin_tablets_taken_2,
                  num_albendzole_pills,
                  num_albendzole_pills_2,
                  num_extra_albendazole,
                  num_extra_albendazole_2,
                  num_extra_ivermectin,
                  num_extra_ivermectin_2,
                  preg_test_result, 
                  preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = everything()) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::group_by(grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(value))

cl_list$efficacy <- efficacy %>% 
    dplyr::mutate(grp = case_when(have_80_480_coartem != 'yes' ~ 'coartem20',
                                   TRUE ~ 'coartem80')) %>% 
    dplyr::group_by(grp) %>% 
    dplyr::summarise(coartem = sum(num_coartem_tablets_given, na.rm = T),
                     coartem_ext = sum(num_extra_coartem_tablets_used, na.rm = T)) %>% 
    dplyr::mutate(stock_used_by_cl = coartem + coartem_ext) %>% 
    dplyr::select(grp, stock_used_by_cl)

stock_used_by_cl <- cl_list %>% 
    purrr::reduce(dplyr::full_join) %>% 
    dplyr::group_by(grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(stock_used_by_cl)) %>% 
    dplyr::select(name = grp, everything())

df <- pharmacy_flow_df %>% 
    dplyr::left_join(pharmacy_sfa_flow_df, by = 'name') %>% 
    dplyr::left_join(pharmacy_fa_flow_df, by = 'name') %>% 
    dplyr::left_join(stock_used_by_cl, by = 'name') %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
  dplyr::mutate(
    pharmacy_stock = pharmacy_arrival - 
      pharmacy_dispatch + 
      pharmacy_return,
    pharmacy_sfa_stock = pharmacy_sfa_arrival - 
      pharmacy_sfa_dispatch + 
      pharmacy_sfa_return,
    pharmacy_fa_stock = pharmacy_fa_arrival - 
      pharmacy_fa_dispatch + 
      pharmacy_fa_return)

```


### a. Bar chart showing stock level

```{r}
plot_df <- df %>% 
    dplyr::select(-contains('_stock'))%>%
    tidyr::pivot_longer(cols = !name, 
                        names_to = 'step',
                        values_to = 'value') %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(step, 'pharmacy_sfa') ~ 'sfa',
                                  stringr::str_detect(step, 'pharmacy_fa') ~ 'fa',
                                  stringr::str_detect(step, 'cl') ~ 'cl',
                                  TRUE ~ 'pharmacy')
                  ) %>% 
    dplyr::mutate(op = case_when(stringr::str_detect(step, 'arrival') ~ 'arrival',
                                  stringr::str_detect(step, 'dispatch') ~ 'dispatch',
                                  stringr::str_detect(step, 'return') ~ 'arrival',
                                 stringr::str_detect(step, 'used') ~ 'used')
                  ) %>%
    group_by(grp, op) %>% 
    summarise(value = sum(value, na.rm =TRUE)) 

plot_1 <- plot_df %>% 
    ggplot(aes(y = grp, x = value, fill = op)) +
    geom_col(position = 'dodge') +
    theme_minimal() +
    scale_fill_brewer(palette = "Paired") +
    labs(x = '')
```



```{r}
plot_df <- df %>% 
    dplyr::select(-contains('_stock'))%>%
    tidyr::pivot_longer(cols = !name, 
                        names_to = 'step',
                        values_to = 'value') %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(step, 'pharmacy_sfa') ~ 'sfa',
                                  stringr::str_detect(step, 'pharmacy_fa') ~ 'fa',
                                  stringr::str_detect(step, 'cl') ~ 'cl',
                                  TRUE ~ 'pharmacy')
                  ) %>% 
    dplyr::mutate(op = case_when(stringr::str_detect(step, 'arrival') ~ 'arrival',
                                  stringr::str_detect(step, 'dispatch') ~ 'dispatch',
                                  stringr::str_detect(step, 'return') ~ 'arrival',
                                 stringr::str_detect(step, 'used') ~ 'used')
                  ) %>%
    group_by(name, op) %>% 
    summarise(value = sum(value, na.rm =TRUE)) 

plot_2 <- plot_df %>% 
    ggplot(aes(y = name, x = value, fill = op)) +
    geom_col(position = 'dodge') +
    theme_minimal() +
    scale_fill_brewer(palette = "Paired") +
    labs(x = '')
```


```{r, fig.width = 9, fig.height=3}
subplot(ggplotly(plot_1), 
        plotly::style(ggplotly(plot_2),showlegend=FALSE), 
        margin = 0.05)
```

### b. Stock & IP Movement

Stock is measured by: `Arrival` - `Dispatch` + `Returns (unused item)`

```{r}
element_id = 'stock_status'
tbl <- reactable(
  df %>% dplyr::select(name, contains('_stock')), 
  elementId = element_id,
  columns = list(
    name = colDef(
      name = "Item", 
      filterable = TRUE
    ),
    pharmacy_stock = colDef(
      name = "Pharmacy Stock"
    ),
    pharmacy_sfa_stock = colDef(
      name = "Pharmacy SFA Stock"
    ),
    pharmacy_fa_stock = colDef(
      name = "Pharmacy FA Stock"
    )),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE
)

wrap_download(
  tbl, 
  element_id,
  'stock.csv')



element_id = 'ip_movement'
tbl <- reactable(
  df %>% dplyr::select(name, everything(), -ends_with('_stock')), 
  elementId = element_id,
  columns = list(
    name = colDef(
      name = "Item", 
      filterable = TRUE
    ),
    pharmacy_arrival = colDef(
      name = "Pharmacy Arrival"
    ),
    pharmacy_dispatch = colDef(
      name = "Pharmacy Dispatch"
    ),
    pharmacy_return = colDef(
      name = "Pharmacy Return"
    ),
    pharmacy_sfa_arrival = colDef(
      name = "Pharmacy SFA Arrival"
    ),
    pharmacy_sfa_dispatch = colDef(
      name = "Pharmacy SFA Dispatch",
      minWidth = 100
    ),
    pharmacy_sfa_return = colDef(
      name = "Pharmacy SFA Return"
    ),
    pharmacy_fa_arrival = colDef(
      name = "Pharmacy FA Arrival"
    ),
    pharmacy_fa_dispatch = colDef(
      name = "Pharmacy FA Dispatch"
    ),
    pharmacy_fa_return = colDef(
      name = "Pharmacy FA Return"
    ),
    stock_used_by_cl = colDef(
      name = "CL Item Used"
    )),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE
)

wrap_download(
  tbl, 
  element_id,
  'ip_movement.csv')
```

### c. Summary table - IP movement sFA by Worker

```{r}
element_id = 'wid_sfa'

## pharmacy
data_list <- list()

# pharmacy initial stock
data_list$pharmacy_sfa <- pharmacy_sfa %>% 
    dplyr::select(
      id_username,
      operation,
      alb_tabsno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno,
      starts_with('unused'),
      unusable_coartem24_no) %>%
    tidyr::pivot_longer(cols =  -c(id_username, operation)) %>% 
    dplyr::mutate(
      operation = case_when(stringr::str_detect(name, 'unused') ~'return',
                            TRUE ~ operation),
      name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                       stringr::str_detect(name, 'alb') ~ 'alb',
                       stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                       stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                       stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::mutate(across(everything(), ~replace_na(.x, 0))) %>%
    dplyr::mutate(key = glue::glue('{operation}_{name}')) %>% 
    tidyr::pivot_wider(id_cols = c(id_username, name),
                       names_from = operation,
                       values_from = value,
                       values_fn = sum,
                       values_fill = 0) %>%
    dplyr::select(id_username, name, arrival, dispatch, return)

tbl <- reactable(
    data_list$pharmacy_sfa,
    groupBy = c("id_username"),
    columns = list(
        id_username = colDef(
            name = "ID Username", 
            filterable = TRUE),
        name = colDef(
            name = "Item", 
            filterable = TRUE),
        arrival = colDef(
            name = "Arrival",
            aggregate = "sum"
        ),
        dispatch = colDef(
            name = "Dispatch",
            aggregate = "sum"
        ),
        return = colDef(
            name = "FA Unused / Return",
            aggregate = "sum"
        )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'wid_sfa.csv')
```

### d. Summary table - IP movement FA by Worker

```{r}
element_id = 'wid_fa'

## pharmacy
data_list <- list()

# pharmacy initial stock
data_list$pharmacy_fa <- pharmacy_fa %>% 
    dplyr::select(
      id_username,
      operation,
      alb_tabletno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno,
      starts_with('unused'),
      unusable_coartem24_no) %>%
    tidyr::pivot_longer(cols =  -c(id_username, operation)) %>% 
    dplyr::mutate(
      operation = case_when(stringr::str_detect(name, 'unused') ~'return',
                            TRUE ~ operation),
      name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                       stringr::str_detect(name, 'alb') ~ 'alb',
                       stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                       stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                       stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::mutate(across(everything(), ~replace_na(.x, 0))) %>%
    dplyr::mutate(key = glue::glue('{operation}_{name}')) %>% 
    tidyr::pivot_wider(id_cols = c(id_username, name),
                       names_from = operation,
                       values_from = value,
                       values_fn = sum,
                       values_fill = 0) %>%
    dplyr::select(id_username, name, arrival, dispatch, return)

tbl <- reactable(
    data_list$pharmacy_fa,
    groupBy = c("id_username"),
    columns = list(
        id_username = colDef(
            name = "ID Username", 
            filterable = TRUE),
        name = colDef(
            name = "Item", 
            filterable = TRUE),
        arrival = colDef(
            name = "Arrival",
            aggregate = "sum"
        ),
        dispatch = colDef(
            name = "Dispatch",
            aggregate = "sum"
        ),
        return = colDef(
            name = "CL Unused / Return",
            aggregate = "sum"
        )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'wid_fa.csv')
```

### e. Summary table - IP movement CL

```{r}
element_id = 'wid_cl'

# Meds used
cl1 <- safety %>% 
    dplyr::inner_join(
      safety_repeat_individual, by = c('KEY' = 'PARENT_KEY')) %>% 
    dplyr::select(
      wid,todays_date,
      num_ivermectin_tablets_taken,
                  num_ivermectin_tablets_taken_2,
                  num_albendzole_pills,
                  num_albendzole_pills_2,
                  num_extra_albendazole,
                  num_extra_albendazole_2,
                  num_extra_ivermectin,
                  num_extra_ivermectin_2,
                  preg_test_result, 
                  preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = -c(wid,todays_date)) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::group_by(wid, todays_date, grp) %>% 
    dplyr::summarise(value = sum(value)) %>% 
    dplyr::mutate(wid = as.character(wid))


cl2 <- safetynew %>% 
    dplyr::inner_join(
      safetynew_repeat_individual, by = c('KEY' = 'PARENT_KEY')) %>% 
    dplyr::select(
      wid,todays_date,
      num_ivermectin_tablets_taken,
                  num_ivermectin_tablets_taken_2,
                  num_albendzole_pills,
                  num_albendzole_pills_2,
                  num_extra_albendazole,
                  num_extra_albendazole_2,
                  num_extra_ivermectin,
                  num_extra_ivermectin_2,
                  preg_test_result, 
                  preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = -c(wid,todays_date)) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::group_by(wid, todays_date, grp) %>% 
    dplyr::summarise(value = sum(value)) %>% 
    dplyr::mutate(wid = as.character(wid))

cl3 <- efficacy %>% 
    dplyr::mutate(grp = case_when(have_80_480_coartem != 'yes' ~ 'coartem20',
                                   TRUE ~ 'coartem80')) %>% 
    dplyr::group_by(wid, todays_date, grp) %>% 
    dplyr::summarise(coartem = sum(num_coartem_tablets_given, na.rm = T),
                     coartem_ext = sum(num_extra_coartem_tablets_used, na.rm = T)) %>% 
    dplyr::mutate(value = coartem + coartem_ext) %>% 
    dplyr::select(wid, todays_date, grp, value) %>% 
    dplyr::mutate(wid = as.character(wid))

df <- dplyr::bind_rows(cl1, cl2, cl3)


tbl <- reactable(
    df,
    groupBy = c("wid"),
    columns = list(
      wid = colDef(
            name = "wid", 
            filterable = TRUE),
      todays_date = colDef(
            name = "Date",
      ),
      grp = colDef(
            name = "Item",
            filterable = TRUE
      ),
      value = colDef(
            name = "Used",
            aggregate = "sum"
      )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'wid_cl.csv')
```

