---
title: "Pharmacy Reports"
description: |
  Reporting used to track SE and PFU
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

Notes:

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT
- Please reach out to atediarjo@gmail.com for bug reports

Description:

This report is used for Pharmacy based on this [Reporting Document](https://docs.google.com/document/d/15-BOyB24J81B7JwMggHYBmX8RGpoC4raIKk8TOkdrf0/edit#heading=h.vk0h181v4mre)

Disclaimer: 

Only `safety`, `safetynew` is used for CL reporting. Thus there is only ALB being reported from site.


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tidyr)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
```

```{r}
INPUT_KEY <- list(
  sepk_icf_verification = glue::glue('{SE_FOLDER_TARGET}/sepk_icf_verification/sepk_icf_verification.csv'),
  sepk_icf_resolution =  glue::glue('{SE_FOLDER_TARGET}/sepk_icf_resolution/sepk_icf_resolution.csv'),
  safety = glue::glue('{SE_FOLDER_TARGET}/safety/safety.csv'),
  safetynew = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew.csv'),
  efficacy =  glue::glue('{SE_FOLDER_TARGET}/efficacy/efficacy.csv'),
  pkday0 =  glue::glue('{SE_FOLDER_TARGET}/pkday0/pkday0.csv')
)


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}
```


```{r}
#################################
# Fetch v0 demography
#################################
pharmacy_fa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_fa/pharmacy_fa.csv'
) %>%
  pad_hhid() %>% 
    tidyr::separate_rows(iptype, sep = " ")

pharmacy_sfa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_sfa/pharmacy_sfa.csv'
) %>%
  pad_hhid() %>% 
    tidyr::separate_rows(iptype, sep = " ")

pharmacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy/pharmacy.csv'
) %>%
  pad_hhid() %>% 
    tidyr::separate_rows(iptype, sep = " ")

v0_repeat <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv'
) %>%
  pad_hhid() 


efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/efficacy/efficacy.csv')) %>%
  pad_hhid()

safety <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety.csv')) %>%
  pad_hhid()

safetynew <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew.csv')) %>%
  pad_hhid()

safety_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety-repeat_individual.csv')) %>%
  pad_hhid()

safetynew_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew-repeat_individual.csv')) %>%
  pad_hhid()


assignment <- cloudbrewr::aws_s3_get_table(
  bucket = 'bohemia-lake-db',
  key = glue::glue('bohemia_prod/dim_arm_assignment/assignments.csv')) %>%
  pad_hhid()
```

### a. Bar chart showing stock level

```{r}
data_list <- list()

data_list$pharmacy <- pharmacy %>%
    dplyr::group_by(operation) %>% 
    dplyr::summarise(n = n_distinct(instanceID)) %>% 
    dplyr::mutate(source = 'pharmacy')

data_list$pharmacy_sfa <- pharmacy_sfa %>%
    dplyr::group_by(operation) %>% 
    dplyr::summarise(n =n_distinct(instanceID)) %>% 
    dplyr::mutate(source = 'pharmacy_sfa')

data_list$pharmacy_fa <- pharmacy_fa %>%
    dplyr::group_by(operation) %>% 
    dplyr::summarise(n = n_distinct(instanceID)) %>% 
    dplyr::mutate(source = 'pharmacy_fa')


plot_1 <- data_list %>% 
  purrr::reduce(dplyr::bind_rows)  %>% 
    ggplot(aes(y = source, x = n, fill = operation)) +
    geom_col(position = 'dodge') +
    theme_minimal() +
    scale_fill_brewer(palette = "Paired")
```



```{r}
p1 <- pharmacy %>%
    dplyr::group_by(iptype, operation) %>% 
    dplyr::summarise(n = n()) %>% dplyr::ungroup()
p2 <- pharmacy_sfa %>%
    dplyr::group_by(iptype, operation) %>% 
    dplyr::summarise(n= n()) %>% dplyr::ungroup()
p3 <- pharmacy_fa %>%
    dplyr::group_by(iptype, operation) %>% 
    dplyr::summarise(n = n()) %>% dplyr::ungroup()
 
plot_2 <- dplyr::bind_rows(p1,p2,p3) %>% 
    dplyr::group_by(iptype, operation) %>% 
    dplyr::summarise(n = sum(n)) %>% 
    ggplot(aes(y = iptype, x = n, fill = operation)) +
    geom_col(position = 'dodge') +
    theme_minimal() +
    scale_fill_brewer(palette = "Paired")
```


```{r, fig.width = 9, fig.height=3}
subplot(ggplotly(plot_1), 
        style(ggplotly(plot_2),showlegend=FALSE), 
        margin = 0.05)
```


```{r}

data_list <- list()

data_list$p1 <- p1 %>% 
    tidyr::pivot_wider(id_cols = 'iptype', 
                       names_from = 'operation', 
                       values_from = 'n') %>% 
    dplyr::mutate(arrival = replace_na(arrival, 0),
                  dispatch = replace_na(dispatch,0)) %>% 
    dplyr::mutate(current_stock = arrival - dispatch) %>% 
    dplyr::select(
      iptype, 
      `Stock received at pharmacy` = arrival, 
      `Stock sent out to field` = dispatch)


data_list$p2 <-p2 %>% 
    tidyr::pivot_wider(id_cols = 'iptype', 
                       names_from = 'operation', 
                       values_from = 'n') %>% 
    dplyr::mutate(arrival = replace_na(arrival, 0),
                  dispatch = replace_na(dispatch,0)) %>% 
    dplyr::mutate(current_stock = arrival - dispatch) %>% 
    dplyr::select(
      iptype, 
      `Stock received by sfa` = arrival, 
      `Stock sent out to fa` = dispatch)

data_list$p3 <- p3 %>% 
    tidyr::pivot_wider(id_cols = 'iptype', 
                       names_from = 'operation', 
                       values_from = 'n') %>% 
    dplyr::mutate(arrival = replace_na(arrival, 0),
                  dispatch = replace_na(dispatch,0)) %>% 
    dplyr::mutate(current_stock = arrival - dispatch) %>% 
    dplyr::select(
      iptype, 
      `Stock sent out to CL` = dispatch)

data_list$p4 <- safety_repeat_individual %>% 
    dplyr::select(num_albendzole_pills) %>% 
    tidyr::drop_na(num_albendzole_pills) %>%
    dplyr::summarise(`Stock dispensed to participants` = n()) %>%
    dplyr::mutate(iptype = 'ALB')

df <- data_list %>% 
    purrr::reduce(dplyr::full_join) %>% 
  mutate(
    across(everything(), ~replace_na(.x, 0))
  )

```

### b. Pharmacy Status

```{r}
element_id = 'pharmacy_status'
tbl <- reactable(
  df %>% 
  dplyr::mutate(
    current_stock = 
      `Stock received at pharmacy` - `Stock sent out to field`) %>% 
    dplyr::select(
        iptype,
        `Stock received at pharmacy`,
        `Stock sent out to field`,
        `Current Stock at Pharmacy` = current_stock
    ),
  elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'pharmacy_status.csv')
```

### c. Summary table - IP movement

```{r}
element_id = 'ip_movement'

tbl <- reactable(df, elementId = element_id)

wrap_download(
  tbl, 
  element_id,
  'ip_movement.csv')
```

### d. Summary table - IP movement sFA

```{r}
element_id = 'ip_movement_sfa'

t <- pharmacy_sfa %>% 
    dplyr::select(id_username, iptype, operation) %>% 
    dplyr::mutate(value = 1) %>%
    tidyr::pivot_wider(id_cols = c(id_username, iptype), 
                       names_from = operation,
                       values_from = value,
                       values_fn = sum
                    )

tbl <- reactable(
    t,
    groupBy = c("id_username", "iptype"),
    columns = list(
        id_username = colDef(
            name = "ID Username", 
            filterable = TRUE),
        arrival = colDef(
            name = "Arrival",
            aggregate = "sum"
        ),
        dispatch = colDef(
            name = "Dispatch",
            aggregate = "sum"
        )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'ip_movement_sfa.csv')
```


### e. Summary table - IP movement FA

```{r}
element_id = 'ip_movement_fa'

t <- pharmacy_fa %>% 
    dplyr::filter(source_entry != 'cl') %>%
    dplyr::select(id_username, iptype, operation) %>% 
    dplyr::mutate(value = 1) %>%
    tidyr::pivot_wider(id_cols = c(id_username, iptype), 
                       names_from = operation,
                       values_from = value,
                       values_fn = sum
                    )

tbl <- reactable(
    t,
    groupBy = c("id_username", "iptype"),
    columns = list(
        id_username = colDef(
            name = "ID Username", 
            filterable = TRUE),
        arrival = colDef(
            name = "Arrival",
            aggregate = "sum"
        ),
        dispatch = colDef(
            name = "Dispatch",
            aggregate = "sum"
        )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'ip_movement_fa.csv')
```

### f. Summary table - IP movement CL

```{r}
element_id = 'ip_movement_cl'

# Data to CL
data_to_cl <- pharmacy_fa %>% 
    dplyr::select(cl_wid_sending, iptype, todays_date) %>% 
    dplyr::group_by(cl_wid_sending, iptype, todays_date) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::ungroup() %>%
    tidyr::separate(col = 'cl_wid_sending', 
                    sep = ' - ', into = c('wid', 'name'), remove = FALSE) %>% 
    dplyr::select(wid, todays_date, iptype, n) %>% 
    tidyr::pivot_wider(
        id_cols = c(wid, todays_date), 
        names_from = iptype, 
        values_from = n, 
        values_fn = sum, 
        values_fill = 0)

# Meds used
cl1 <- safety %>% 
    dplyr::inner_join(
      safety_repeat_individual, by = c('KEY' = 'PARENT_KEY')) %>% 
    dplyr::group_by(wid, todays_date) %>% 
    dplyr::summarise(ALB = sum(num_albendzole_pills, na.rm = T)) %>% 
    tidyr::drop_na() %>% 
    dplyr::mutate(wid = as.character(wid))


cl2 <- safetynew %>% 
    dplyr::inner_join(
      safetynew_repeat_individual, by = c('KEY' = 'PARENT_KEY')) %>% 
    dplyr::group_by(wid, todays_date) %>% 
    dplyr::summarise(ALB = sum(num_albendzole_pills, na.rm = T)) %>% 
    tidyr::drop_na() %>% 
    dplyr::mutate(wid = as.character(wid))

cl_used <- dplyr::bind_rows(cl1,cl2) %>% 
    dplyr::group_by(wid, todays_date) %>% 
    dplyr::summarise(ALB = sum(ALB)) %>% 
    dplyr::mutate(pRDT = 0,
                  IVM = 0)

df <- data_to_cl %>% 
    dplyr::full_join(cl_used, by = c('wid', 'todays_date')) %>%
    dplyr::select(wid, 
                  todays_date,
                  starts_with('ALB'), 
                  starts_with('pRDT'), 
                  starts_with('IVM'))



tbl <- reactable(
    df,
    groupBy = c("wid"),
    columns = list(
      wid = colDef(
            name = "wid", 
            filterable = TRUE),
      todays_date = colDef(
            name = "Date",
      ),
      ALB.x = colDef(
            name = "ALB Received",
            aggregate = "sum"
      ),
      ALB.y = colDef(
            name = "ALB Used",
            aggregate = "sum"
      ),
      IVM.x = colDef(
            name = "IVM Received",
            aggregate = "sum"
      ),
      IVM.y = colDef(
            name = "IVM Used",
            aggregate = "sum"
      ),
      pRDT.x = colDef(
            name = "pRDT Received",
            aggregate = "sum"
      ),
      pRDT.y = colDef(
            name = "pRDT Used",
            aggregate = "sum"
      )
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  'ip_movement_fa.csv')
```

