---
title: "Kwale V0 Demography Report"
description: |
  Reporting used to track V0 demography data collection in Kwale
output:
  html_document:
    toc: true
    theme: cerulean
date: '`r Sys.time()`'
---

Notes:

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT
- Please reach out to atediarjo@gmail.com for bug reports

Dictionary:

- Absences: **refusal_or_absence in 'Absence 2nd attempt', 'Household is destroyed/abandoned', 'Emancipated minor'**
- Refusals: **refusal_or_absence equals 'Refusal'**

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
```

```{r, echo = FALSE, message=FALSE}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
  tagList(
    tags$button(
      tagList(fontawesome::fa("download"), "Download as CSV"),
      onclick = onclick_command),
    reactable_obj
  ))
}
```


```{r}
# variables / creds for ento
env_pipeline_stage <- Sys.getenv("PIPELINE_STAGE")
bucket_source <- 'databrew.org'
bucket_lake_db <- 'bohemia-lake-db'
input_key <- list(
  v0 = 'kwale/clean-form/v0demography/v0demography.csv',
  v0_repeat = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv',
  sev0rab = 'kwale/clean-form/sev0rab/sev0rab.csv',
  sev0ra = 'kwale/clean-form/sev0ra/sev0ra.csv',
  goals = 'bohemia_prod/dim_kwale_cluster_goal/dim_kwale_cluster_goal.csv'
)
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = env_pipeline_stage)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```
```{r}
v0demography <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$v0)

v0demography_repeat <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$v0_repeat)

goals <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_lake_db,
  key = input_key$goals)

sev0rab <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$sev0rab)
sev0ra <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$sev0ra)

sev0ra_joined <- dplyr::bind_rows(sev0ra, sev0rab) %>% 
    dplyr::filter(!hhid %in% unique(v0demography$hhid) | is.na(hhid))

absences <- sev0ra_joined %>% 
    dplyr::filter(refusal_or_absence %in% c("Absence 2nd attempt",
                                            "Emancipated minor",
                                            'Household is destroyed/abandoned'))
refusals <-  sev0ra_joined %>% 
    dplyr::filter(refusal_or_absence %in% c("Refusal"))
```


## Submission Summary

```{r}
submission_hh <- v0demography %>% 
  distinct(hhid) %>% 
  nrow()
target_hh <- goals$households_core_and_buffer %>% sum()


submission_hh_members <- sum(v0demography$num_hh_members)
target_hh_members <- goals$members_core_and_buffer %>% sum()
submission_refusals <- nrow(refusals)
submission_absences <- nrow(absences)

summary <-  tibble(
  submission_hh = submission_hh,
  target_hh = target_hh,
  submission_hh_members = submission_hh_members,
  target_hh_members = target_hh_members,
  submission_absences = submission_absences,
  submission_refusals = submission_refusals
) %>%
  dplyr::mutate(
    coverage_hh = submission_hh / target_hh,
    coverage_hh_members = submission_hh_members / target_hh_members,
  ) %>%
  dplyr::select(submission_hh, 
                target_hh,
                coverage_hh, 
                submission_hh_members, 
                target_hh_members, 
                coverage_hh_members,
                submission_absences,
                submission_refusals)

tbl <- reactable(
    summary,
    columns = list(
        submission_hh = colDef(name = 'Household Submission'),
        target_hh = colDef(name = "Target Household Submission"),
        coverage_hh = colDef(
            name = 'Household Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        submission_hh_members = colDef(name = 'Household Member Submission'),
        target_hh_members = colDef(name = "Target Household Member Submission"),
        coverage_hh_members = colDef(
            name = 'Household Member Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        submission_absences = colDef(name = 'Absences'),
        submission_refusals = colDef(name = 'Refusals')
        
    ),
    highlight = TRUE
)

tbl
```


## Submissions by day
```{r, fig.width=10, fig.height=3}
submissions <- v0demography %>% 
    dplyr::mutate(metric_date = lubridate::date(SubmissionDate)) %>% 
    dplyr::group_by(metric_date) %>% 
    dplyr::summarise(n_submission = n_distinct(hhid))%>%
    dplyr::select(`date` = metric_date,
                  `submission` = n_submission)

submissions_by_dow <- submissions %>% 
    dplyr::mutate(dow = lubridate::wday(date, label = TRUE)) %>%
    dplyr::group_by(dow) %>%
    dplyr::summarise(submission = sum(submission))

p1 <- submissions %>%
    ggplot(aes(x = `date`, y = `submission`)) +
    geom_line() +
    geom_point() + 
    theme_minimal() +
    labs(
      y = 'Submissions', 
      x = '')

p2 <- submissions_by_dow %>%
    ggplot(aes(x = `dow`, y = `submission`)) +
    geom_col() + 
    theme_minimal() +
    labs(
      y = 'Submissions', 
      x = '')

subplot(ggplotly(p1), ggplotly(p2))
```

```{r}
element_id <- 'submission-by-day'
tbl <- reactable(submissions,
          columns = list(
            date = colDef(name = 'Date', filterable = TRUE),
            submission = colDef(name = 'Submission')
          ),
    highlight = TRUE,
    striped = TRUE,
    elementId = 'submission-by-day'
)

wrap_download(
  tbl, 
  element_id,
  'v0_demography_submission_tracker.csv')
```


## Field Assistant Tracker
```{r}
element_id <- 'fa-tracker'
submission <- v0demography %>% 
    dplyr::group_by(cluster, fa_id)%>%
    dplyr::summarise(
      hh = n_distinct(hhid),
      hh_members = sum(num_hh_members)
    )

absences_df <- absences %>% 
    dplyr::group_by(cluster) %>% 
    dplyr::summarise(hh_absences = n())

refusals_df <- refusals %>% 
    dplyr::group_by(cluster) %>% 
    dplyr::summarise(hh_refusal = n())

target <- goals %>%
  dplyr::group_by(cluster_number) %>%
  dplyr::summarise(target_hh = sum(households_core_and_buffer),
                   target_hh_members = sum(members_core_and_buffer)) %>% 
  dplyr::select(cluster = cluster_number, everything())

summary <- target %>%
  dplyr::left_join(submission)  %>%
  dplyr::left_join(absences_df) %>%
  dplyr::left_join(refusals_df) %>%
  dplyr::mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  dplyr::select(-cluster) %>%
  dplyr::group_by(fa_id) %>% 
  dplyr::summarise_all(sum) %>%
  dplyr::mutate(
    hh_total = hh + hh_absences + hh_refusal,
    hh_total_coverage = (hh_total / target_hh),
    hh_coverage = (hh / target_hh),
    hh_members_coverage = (hh / target_hh_members)
  ) %>% 
  dplyr::select(fa_id,
                target_hh,
                target_hh_members,
                hh,
                hh_coverage,
                hh_members,
                hh_members_coverage,
                hh_absences,
                hh_refusal,
                hh_total,
                hh_total_coverage)

tbl <- reactable(
    summary,
    columns = list(
        fa_id = colDef(name = 'Field Assistant ID', filterable = TRUE),
        target_hh = colDef(name = "Target Household Submission"),
        target_hh_members = colDef(name = "Target Household Member Submission"),
        hh = colDef(name = "Household Submission"),
        hh_members = colDef(name = "Household Members"),
        hh_coverage = colDef(
            name = 'Household Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        hh_members_coverage = colDef(
            name = 'Household Members Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        hh_absences = colDef(name = "Absences"),
        hh_refusal = colDef(name = "Refusals"),
        hh_total = colDef(name = "Household Submissions + Absences and Refusals"),
        hh_total_coverage = colDef(
            name = 'Household Total Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            })
    ),
    columnGroups = list(
      colGroup(name = "Target", 
               columns = c('target_hh', 'target_hh_members')),
      colGroup(name = "Visits", 
               columns = c('hh', 'hh_coverage', 'hh_members', 'hh_members_coverage')),
      colGroup(name = "Absences and Refusals", 
               columns = c('hh_absences', 'hh_refusal')),
      colGroup(name = "Total Coverage", 
               columns = c('hh_total','hh_total_coverage'))
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)


wrap_download(tbl, 
              element_id, 
              'v0_demography_fa_tracker.csv')

```


## Cluster Coverage Tracker

```{r}
element_id <- 'cluster-tracker'
submission <- v0demography %>% 
    dplyr::group_by(cluster, fa_id)%>%
    dplyr::summarise(
      hh = n_distinct(hhid),
      hh_members = sum(num_hh_members)
    )

absences_df <- absences %>% 
    dplyr::group_by(cluster) %>% 
    dplyr::summarise(hh_absences = n())

refusals_df <- refusals %>% 
    dplyr::group_by(cluster) %>% 
    dplyr::summarise(hh_refusal = n())

target <- goals %>%
  dplyr::group_by(cluster_number) %>%
  dplyr::summarise(target_hh = sum(households_core_and_buffer),
                   target_hh_members = sum(members_core_and_buffer)) %>% 
  dplyr::select(cluster = cluster_number, everything())

summary <- target %>%
  dplyr::left_join(submission)  %>%
  dplyr::left_join(absences_df) %>%
  dplyr::left_join(refusals_df) %>%
  dplyr::mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  dplyr::mutate(
    hh_total = hh + hh_absences + hh_refusal,
    hh_total_coverage = (hh_total / target_hh),
    hh_coverage = (hh / target_hh),
    hh_members_coverage = (hh / target_hh_members)
  ) %>% 
  dplyr::select(cluster, 
                fa_id,
                target_hh,
                target_hh_members,
                hh,
                hh_coverage,
                hh_members,
                hh_members_coverage,
                hh_absences,
                hh_refusal,
                hh_total,
                hh_total_coverage)

tbl <- reactable(
    summary,
    columns = list(
        cluster = colDef(name = 'Cluster Number', filterable = TRUE),
        fa_id = colDef(name = 'Field Assistant ID', filterable = TRUE),
        target_hh = colDef(name = "Target Household Submission"),
        target_hh_members = colDef(name = "Target Household Member Submission"),
        hh = colDef(name = "Household Submission"),
        hh_members = colDef(name = "Household Members"),
        hh_coverage = colDef(
            name = 'Household Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        hh_members_coverage = colDef(
            name = 'Household Members Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            }),
        hh_absences = colDef(name = "Absences"),
        hh_refusal = colDef(name = "Refusals"),
        hh_total = colDef(name = "Household Submissions + Absences and Refusals"),
        hh_total_coverage = colDef(
            name = 'Household Total Coverage %',
            format = colFormat(percent = TRUE, digits = 1),
            style = function(value) {
                if (value >= 1) {
                    color <- "#008000"
                } else if (value < 1) {
                    color <- "#e00000"
                } else {
                    color <- "#777"
                }
                list(color = color, fontWeight = "bold")
            })
    ),
    columnGroups = list(
      colGroup(name = "Target", 
               columns = c('target_hh', 'target_hh_members')),
      colGroup(name = "Visits", 
               columns = c('hh', 'hh_coverage', 'hh_members', 'hh_members_coverage')),
      colGroup(name = "Absences and Refusals", 
               columns = c('hh_absences', 'hh_refusal')),
      colGroup(name = "Total Coverage", 
               columns = c('hh_total','hh_total_coverage'))
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)


wrap_download(tbl, 
              element_id, 
              'v0_demography_cluster_tracker.csv')
```


## Attendance List

```{r}
element_id <- 'attendance-tracker'
attendance <- v0demography %>% 
    dplyr::mutate(metric_date = lubridate::date(SubmissionDate)) %>% 
    dplyr::group_by(fa_id, metric_date) %>% 
    dplyr::summarise(n_submission = n_distinct(hhid)) %>%
    dplyr::ungroup() %>%
    dplyr::select(
      fa_id,
      date = metric_date,
      submission = n_submission)

tbl <- reactable(
  attendance,
  groupBy = "fa_id",
  columns = list(
    fa_id= colDef(name = "Field Assistant ID", filterable = TRUE),
    date = colDef(
      name = "Submitted Date",
      aggregate = "count",
      format = list(
        aggregated = colFormat(suffix = " dates")
      )
    ),
    submission = colDef(
      name = "Submissions",
      aggregate = "sum"
    )
  ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    elementId = element_id
)

wrap_download(tbl, 
              element_id, 
              'v0_demography_attendance_tracker.csv')
```
