---
title: "ICF V0 Reports"
description: |
  Reporting used to track V0 demography data collection in Kwale
output:
  html_document:
    toc: true
    theme: cerulean
date: '`r Sys.time()`'
---

Notes:

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT
- Please reach out to atediarjo@gmail.com for bug reports

Description:

This report is used for ICF monitoring based on this [Reporting Document](https://docs.google.com/document/d/16w7fjTfRJZZRWa99PM49hrk1Sr6IRInSmQTqz4YwVVQ/edit)

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
```

```{r, echo = FALSE, message=FALSE}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
  tagList(
    tags$button(
      tagList(fontawesome::fa("download"), "Download as CSV"),
      onclick = onclick_command),
    reactable_obj
  ))
}
```


```{r}
# variables / creds for ento
env_pipeline_stage <- Sys.getenv("PIPELINE_STAGE")
bucket_source <- 'databrew.org'
bucket_lake_db <- 'bohemia-lake-db'
input_key <- list(
  v0 = 'kwale/clean-form/v0demography/v0demography.csv',
  v0_repeat = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv',
  icf_resolution = 'kwale/clean-form/demography_icf_resolutions/demography_icf_resolutions.csv',
  icf_verification = 'kwale/clean-form/demography_icf_verification/demography_icf_verification.csv',
  goals = 'bohemia_prod/dim_kwale_cluster_goal/dim_kwale_cluster_goal.csv'
)
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = env_pipeline_stage)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```


```{r}
v0demography <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$v0)

v0demography_repeat <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$v0_repeat)

icf_resolutions <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$icf_resolution)

icf_verification <- cloudbrewr::aws_s3_get_table(
  bucket = bucket_source,
  key = input_key$icf_verification)
```


```{r}

icf_ver <- icf_verification %>%
     dplyr::mutate(hhid = as.integer(hhid),
                   icf_submission_date = SubmissionDate,
                   hh_icf_status = as.character(hh_icf_stat)) %>%
      dplyr::group_by(hhid) %>%
      dplyr::filter(SubmissionDate == max(SubmissionDate, na.rm=T)) %>%
      dplyr::ungroup() %>%
      dplyr::select(hhid,
                    archivist_id, 
                    icf_submission_date = SubmissionDate, 
                    hh_icf_status = hh_icf_stat) %>%
      dplyr::mutate(source_id = 'demography_icf_verification')

# icf_res <- icf_resolutions %>% 
#     dplyr::mutate(hhid = as.integer(hhid),
#                   archivist_id = NA_character_,
#                   icf_submission_date = lubridate::as_datetime(SubmissionDate),
#                   hh_icf_status = as.character(hh_icf_status)) %>% 
#     dplyr::select(hhid, archivist_id, icf_submission_date, hh_icf_status) %>%
#     dplyr::mutate(stage = 'resolution')

# most_recent_icf_status <- combined %>% 
#     dplyr::group_by(hhid) %>% 
#     dplyr::filter(SubmissionDate == max(SubmissionDate)) %>% 
#     dplyr::ungroup() %>% 
#     dplyr::select(hhid, icf_submission_date = SubmissionDate, hh_icf_status)


icf_base <- v0demography_repeat %>%
    dplyr::mutate(participant_id = case_when(
      person_signed_icf_yn == 'yes' ~ person_signed_icf,
      TRUE ~ NA_character_)) %>%
    dplyr::filter(person_signed_icf_yn == 'yes') %>%
    dplyr::right_join(v0demography %>% 
                          dplyr::select(KEY, 
                                        hhid, 
                                        cluster, 
                                        fa_id, 
                                        wid,
                                        icf_completed, 
                                        v0_submission_date = todays_date), 
                      by = c('PARENT_KEY' = 'KEY') 
                     ) %>% 
    dplyr::select(participant_id,
                  age,
                  extid, 
                  hhid, 
                  cluster,
                  wid,
                  fa_id, 
                  icf_completed,
                  v0_submission_date) %>%
    dplyr::mutate(icf_completed = ifelse(icf_completed == 1, 'yes', 'no')) %>% 
    dplyr::left_join(icf_ver, by = 'hhid')

```


### ICF Table

- This table can be used to cover requirement on ICF information at different stages
- You can filter ICF based on different ICF Status Unresolved/Archived/Lost-Not Found/Resolved-Archived based on your use cases

```{r}
element_id <- 'all_icf_report'

tbl <- reactable(
  icf_base,
  columns = list(
    participant_id = colDef(name = "Participant ID"),
    age = colDef(name = "Age"),
    extid = colDef(name = "Ext ID"),
    hhid = colDef(name = "HH ID"),
    cluster = colDef(name = "Cluster"),
    wid = colDef(name = "CL ID"),
    fa_id = colDef(name = "FA ID"),
    icf_completed = colDef(name = "ICF Completed"),
    v0_submission_date  = colDef(name = "V0 Submission Date"),
    archivist_id = colDef(name = "Archivist ID"),
    icf_submission_date = colDef(name = "ICF Submission Date"),
    hh_icf_status = colDef(name = "ICF Status (Verification & Resolutions)"),
    source_id = colDef(name = "ICF Source")
  ),
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = TRUE,
  filterable = TRUE,
  wrap = TRUE,
  elementId = element_id)

wrap_download(tbl, 
              element_id, 
              'icf_table_all.csv')
```

