---
title: "ICF Safety & Efficacy / PK Reports"
description: |
  Reporting used to track ICF in Safety/Efficacy & PK
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

## Getting Started

This report is used for ICF monitoring based on this [Reporting Document](https://docs.google.com/document/d/1WvrQ7EDnFFL87iL5reFgKC6dGWA5EEzgma-gLuSZWKQ/edit#heading=h.qmggsikczir8)

#### Refresh Rate

**This report will be updated every 9-5PM EAT and once 12AM EAT**

#### Bug Reports

Please report bug to `e.elobolobo@gmail.com` / `atediarjo@gmail.com`


#### ICF Statuses Intro

1. Unverified: These are individuals with copy of ICF forms given in a visit, but not available in ICF verification

2. Unverified (> 20 days): These are individuals with copy of ICF forms given in a visit, but not available in ICF verification for more than 20 days

3. Missing / Unverified (> 30 days): These are individuals with copy of ICF forms given in a visit, but not available in ICF verification for more than 30 days - which we consider as missing now

4. Unresolved: These are individuals that have been verified, but has an `ICF stat = Rectification` and will require resolution

5. Unresolved (>20 days): These are individuals that have been verified, but has an `ICF stat = Rectification` for more than 20 days

6. Resolved: These are individuals that have been verified, but has an `ICF stat = Rectification` and has been resolved by Fieldworkers

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(formattable)
library(lubridate)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
```


```{r}
INPUT_KEY <- list(
    v0 = glue::glue('{SE_FOLDER_TARGET}/v0demography/v0demography.csv'),
    v0_repeat = glue::glue('{SE_FOLDER_TARGET}/v0demography/v0demography-repeat_individual.csv'),
    sepk_icf_verification = glue::glue('{SE_FOLDER_TARGET}/sepk_icf_verification/sepk_icf_verification.csv'),
    # sepk_icf_resolution =  glue::glue('{SE_FOLDER_TARGET}/sepk_icf_resolution/sepk_icf_resolution.csv'),
    safety = glue::glue('{SE_FOLDER_TARGET}/safety/safety.csv'),
    safetynew = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew.csv'),
    safety_repeat_individual = glue::glue('{SE_FOLDER_TARGET}/safety/safety-repeat_individual.csv'),
    safetynew_repeat_individual = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew-repeat_individual.csv'),
    efficacy =  glue::glue('{SE_FOLDER_TARGET}/efficacy/efficacy.csv')
  )


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}

create_snapshot_tbl <- function(data){
  min_date <- lubridate::floor_date(
    (data$SubmissionDate %>% lubridate::date() %>% min()),
    unit = 'weeks'
  )
  max_date <- lubridate::today()
  date_list <- seq.Date(min_date, max_date, "weeks")
  data_hist <- purrr::map_dfr(date_list, function(d){
    data %>% 
      dplyr::mutate(run_date = d) %>% 
      dplyr::filter(SubmissionDate <= d)
  })
  
  return(data_hist)
}

pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}
```


```{r}
# get data from AWS
sepk_icf_verification <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/sepk_icf_verification/sepk_icf_verification.csv'
) %>%
  pad_hhid() %>% 
  dplyr::group_by(extid, study_select, icf_stat) %>% 
  dplyr::mutate(max_submission_date = max(SubmissionDate)) %>% 
  dplyr::filter(SubmissionDate == max_submission_date) %>% 
  dplyr::ungroup()

sepk_icf_resolution <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/sepk_icf_resolution/sepk_icf_resolution.csv'
) %>%
  pad_hhid() %>% 
  dplyr::group_by(extid, study_select, icf_stat) %>% 
  dplyr::mutate(max_submission_date = max(SubmissionDate)) %>% 
  dplyr::filter(SubmissionDate == max_submission_date) %>% 
  dplyr::ungroup()

v0demography <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/v0demography/v0demography.csv'
) %>%
  pad_hhid()

v0demography_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv'
) %>%
  pad_hhid()

v0_roster <- v0demography %>% 
    dplyr::inner_join(v0demography_repeat_individual, by = c('KEY' = 'PARENT_KEY')) %>% 
    dplyr::select(extid, hhid, wid, fa_id, dob) %>% 
    dplyr::mutate(age = as.integer(lubridate::date('2023-10-01') - lubridate::date(dob)) / 365.25)


safety <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/safety/safety.csv') %>%
  pad_hhid() 

safety_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/safety/safety-repeat_individual.csv') %>%
  pad_hhid() 

safetynew <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/safetynew/safetynew.csv') %>%
  pad_hhid() 

safetynew_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/safetynew/safetynew-repeat_individual.csv') %>%
  pad_hhid() 

efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/efficacy/efficacy.csv') %>%
  pad_hhid() 
```

```{r}
# Get departures
safety_departures <- safety_repeat_individual %>%
  filter(!is.na(lastname), !is.na(dob)) %>%
  mutate(dob = lubridate::as_datetime(dob)) %>%
  filter(person_left_household == 1| person_migrated == 1 | person_out_migrated == 1) %>%
  left_join(safety %>% dplyr::select(hhid, KEY, start_time), by = c('PARENT_KEY' = 'KEY')) %>%
  dplyr::select(hhid, start_time, firstname, lastname, dob, sex, extid) %>%
  mutate(type = 'Departure') %>%
  mutate(start_time = lubridate::as_datetime(start_time))
safety_deaths <- safety_repeat_individual %>%
  left_join(safety %>% dplyr::select(KEY, start_time, hhid), by = c('PARENT_KEY' = 'KEY')) %>%
  filter(!is.na(lastname), !is.na(dob)) %>%
  mutate(firstname = as.character(firstname), lastname = as.character(lastname),
         sex = as.character(sex), extid = as.character(extid)) %>%
  mutate(start_time = as.POSIXct(start_time)) %>%
  mutate(dob = lubridate::as_datetime(dob)) %>%
  filter(!is.na(person_absent_reason)) %>%
  filter(person_absent_reason %in% c('Died')) %>%
  # filter(person_absent_reason %in% c('Died', 'Migrated')) %>%
  dplyr::select(hhid, start_time, firstname, lastname, dob, sex, extid) %>% mutate(type = 'Died')
# Get efficacy departures (but ignore migrations, per project instructions)
# https://bohemiakenya.slack.com/archives/C042KSRLYUA/p1690186129913529?thread_ts=1689946560.024259&cid=C042KSRLYUA
efficacy_departures <- efficacy %>%
  filter(!is.na(lastname), !is.na(dob)) %>%
  mutate(firstname = as.character(firstname), lastname = as.character(lastname),
         sex = as.character(sex), extid = as.character(extid)) %>%
  mutate(start_time = as.POSIXct(start_time)) %>%
  mutate(dob = lubridate::as_datetime(dob)) %>%
  filter(!is.na(person_absent_reason)) %>%
  filter(person_absent_reason != 'Absent')
efficacy_deaths <- efficacy_departures %>%
  filter(person_absent_reason %in% c('Died')) %>%
  # filter(person_absent_reason %in% c('Died', 'Migrated')) %>%
  dplyr::select(hhid, start_time, firstname, lastname, dob, sex, extid) %>% mutate(type = 'Died')
# Combine safety and efficacy departures
departures <- bind_rows(safety_departures, safety_deaths, efficacy_deaths)
```


```{r}
# create initial roster
safety_roster <- safety %>% 
    dplyr::inner_join(safety_repeat_individual, 
                      by = c('KEY'='PARENT_KEY')) %>% 
    dplyr::filter(ind_icf_completed == 1) %>%
    dplyr::filter(!is.na(ind_read_sign_name)) %>%
    dplyr::mutate(study_select = 'safety',
                  wid = as.character(wid)) %>% 
    dplyr::group_by(extid, study_select) %>% 
    dplyr::mutate(max_visit = max(visit)) %>% 
    dplyr::filter(visit == max_visit) %>%
    dplyr::select(SubmissionDate, 
                  instanceID,
                  wid,
                  hhid, 
                  extid,
                  status = safety_status,
                  icf_completed = ind_icf_completed,
                  visit) %>% 
    dplyr::left_join(v0_roster %>% dplyr::select(extid, age, fa_id), by = c('extid'))

safetynew_roster <- safetynew %>%
    dplyr::inner_join(safetynew_repeat_individual,
                      by = c('KEY'='PARENT_KEY')) %>%
    dplyr::filter(ind_icf_completed == 1) %>% 
    dplyr::filter(!is.na(ind_read_sign_name)) %>%
    dplyr::mutate(study_select = 'safety',
                  wid = as.character(wid)) %>% 
    dplyr::group_by(extid, study_select) %>% 
    dplyr::mutate(max_visit = max(visit)) %>% 
    dplyr::filter(visit == max_visit) %>%
    dplyr::select(SubmissionDate, 
                  instanceID,
                  wid,
                  age,
                  hhid, 
                  extid,
                  status = safety_status,
                  icf_completed = ind_icf_completed,
                  visit) %>% 
    dplyr::left_join(v0_roster %>% dplyr::distinct(hhid, fa_id), by = c('hhid'))

efficacy_roster <- efficacy %>%
    # dplyr::filter(efficacy_status != 'refusal') %>% 
    dplyr::filter(icf_completed == 1) %>%
    dplyr::mutate(study_select = 'efficacy',
                  wid = as.character(wid)) %>% 
    filter(!is.na(person_absent_reason)) %>%
    filter(person_absent_reason == '') %>%
    dplyr::group_by(extid, study_select) %>% 
    dplyr::mutate(max_visit = max(visit)) %>% 
    dplyr::filter(visit == max_visit) %>%
    dplyr::select(SubmissionDate, 
                  instanceID,
                  wid,
                  hhid, 
                  extid,
                  status = efficacy_status,
                  icf_completed,
                  visit) %>% 
    dplyr::left_join(v0_roster %>% dplyr::distinct(extid, age, fa_id), by = c('extid'))


roster <- dplyr::bind_rows(
  safety_roster,
  safetynew_roster,
  efficacy_roster) %>% 
  dplyr::ungroup() %>%
  dplyr::filter(extid != "") %>% 
  dplyr::filter(status %in% c('in', 'eos', 'out'),
                !extid %in% departures$extid)

# get first of occurence from distinct
roster_hist <- roster %>% 
  dplyr::mutate(run_date = lubridate::date(lubridate::now()))
```


```{r}
# merge ICF data
# get most recent submission only
verification <- sepk_icf_verification %>% 
    dplyr::group_by(extid, study_select) %>% 
    dplyr::filter(SubmissionDate == max(SubmissionDate)) %>% 
    dplyr::ungroup() %>%
    dplyr::select(extid, 
                  study_select,
                  instanceID,
                  SubmissionDate, 
                  icf_stat,
                  resolution_needed, 
                  fa_id, 
                  cl_id, 
                  archivist_select,
                  safety_status,
                  efficacy_status,
                  pk_status)


# get most recent submission only
resolution <- sepk_icf_resolution %>% 
    dplyr::group_by(extid, study_select) %>% 
    dplyr::filter(SubmissionDate == max(SubmissionDate)) %>% 
    dplyr::ungroup() %>%
    dplyr::select(extid, 
                  study_select,
                  instanceID,
                  SubmissionDate, 
                  icf_stat,
                  extid, 
                  fa_id, 
                  cl_id, 
                  archivist_select)

icf_roster <- verification %>% 
    dplyr::select(instanceID, SubmissionDate, icf_stat, extid, study_select, fa_id,
                                       cl_id,
                                       archivist_select) %>%
    dplyr::bind_rows(resolution %>% 
                         dplyr::select(instanceID, 
                                       SubmissionDate, 
                                       icf_stat, 
                                       extid, 
                                       study_select,
                                       fa_id,
                                       cl_id,
                                       archivist_select)) %>% 
    dplyr::group_by(extid, study_select) %>% 
    dplyr::mutate(max_submission_date = max(SubmissionDate)) %>% 
    dplyr::ungroup() %>%
    dplyr::filter(SubmissionDate == max_submission_date) %>%
    dplyr::inner_join(roster %>% dplyr::select(extid, study_select, status), 
                      by = c('extid', 'study_select'))

icf_hist <- icf_roster %>%  dplyr::mutate(run_date = lubridate::date(lubridate::now())) 
```


```{r}
# versioning
version <- format(floor_date(lubridate::today(), 'week'), "%Y%m%d")


# data coming from verification
data_list <- list()
final_col_list <- c(
  'run_date', 
  'extid', 
  'instanceID',
  'metric', 
  'metric_aging', 
  'study_select', 
  'status',
  'SubmissionDate'
  )

data_list$safety_unresolved_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Rectification',
      study_select == 'safety') %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Safety ICF Unresolved',
      source = 'Safety ICF') %>% 
    dplyr::select(any_of(final_col_list))

data_list$efficacy_unresolved_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Rectification',
      study_select == 'efficacy',
      status != "") %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Efficacy ICF Unresolved',
      source = 'Efficacy ICF') %>% 
    dplyr::select(any_of(final_col_list))


data_list$safety_resolved_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Resolved-Archived',
      study_select == 'safety') %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = NA,
      metric = 'Safety ICF Resolved',
      source = 'Safety ICF') %>% 
    dplyr::select(any_of(final_col_list))

data_list$efficacy_resolved_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Resolved-Archived',
      study_select == 'efficacy',
      status != "") %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = NA,
      metric = 'Efficacy ICF Resolved',
      source = 'Efficacy ICF') %>% 
    dplyr::select(any_of(final_col_list))


data_list$safety_unverified_icf <- roster_hist %>%
    dplyr::filter(study_select == 'safety') %>%
    dplyr::anti_join(icf_hist, 
                     by = c('run_date','extid', 'study_select')) %>% 
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Safety ICF Unverified',
      source = 'Safety ICF') %>% 
    dplyr::select(any_of(final_col_list))

data_list$efficacy_unverified_icf <- roster_hist %>%
    dplyr::filter(study_select == 'efficacy') %>%
    dplyr::anti_join(icf_hist, 
                     by = c('run_date','extid', 'study_select')) %>% 
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Efficacy ICF Unverified',
      source = 'Efficacy ICF') %>% 
    dplyr::select(any_of(final_col_list))


data_list$safety_missing_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Lost-Not Found',
      study_select == 'safety') %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Safety ICF Missing',
      source = 'Safety ICF') %>% 
    dplyr::select(any_of(final_col_list))

data_list$efficacy_missing_icf <- icf_hist %>% 
    dplyr::filter(
      icf_stat == 'Lost-Not Found',
      study_select == 'efficacy',
      status != "") %>%
    dplyr::mutate(
      SubmissionDate = lubridate::date(SubmissionDate)) %>%
    dplyr::mutate(
      metric_aging = as.numeric(difftime(run_date, SubmissionDate, units = "days")),
      metric = 'Efficacy ICF Missing',
      source = 'Efficacy ICF') %>% 
    dplyr::select(any_of(final_col_list))


d <- purrr::reduce(data_list, dplyr::bind_rows) %>% 
      dplyr::mutate(metric_aging_group = case_when(
        metric == 'Efficacy ICF Unverified' & metric_aging > 30 ~ 
            'Efficacy ICF Missing (Unverified >30 days)',
        metric == 'Safety ICF Unverified' & metric_aging > 30 ~ 
            'Safety ICF Missing (Unverified >30 days)',
        metric == 'Efficacy ICF Unverified' & metric_aging > 20 ~ 
            'Efficacy ICF Unverified >20days',
        metric == 'Safety ICF Unverified' & metric_aging > 20 ~ 
            'Safety ICF Unverified >20days',
        metric == 'Efficacy ICF Unresolved' & metric_aging > 20 ~ 
            'Efficacy ICF Unresolved >20days',
        metric == 'Safety ICF Unresolved' & metric_aging > 20 ~ 
            'Safety ICF Unresolved >20days',
        TRUE ~ metric
    ))
```


## ICF Metrics Table

This detail table can be use to drill-down on issues coming from ICF, there will be information regarding several ICF issues and their corresponding ID (`instanceID`) coming based on each issues. 

**Note**:

`instanceID` and `SubmissionDate` are fields coming from different table sources:

- For `unresolved` ICF submission date came from verification form

- For `unverified` ICF submission date came from safety/efficacy/pk form

- For `missing` ICF submission date came from safety/efficacy/pk form


```{r}
c_data <- d %>%
    dplyr::filter(run_date == max(.$run_date)) %>% 
    dplyr::mutate(age = as.numeric(metric_aging),
                  source = study_select) %>% 
    dplyr::left_join(roster %>% dplyr::select(extid, 
                                              study_select, 
                                              `Worker ID` = wid, 
                                              `FA ID` = fa_id, 
                                              `Participant Age` = age,
                                              visit), by = c('extid','study_select'))
```

```{r}
data <- c_data %>% 
    dplyr::mutate(metric = coalesce(metric_aging_group, metric)) %>%
    dplyr::select(-metric_aging_group, -age, -source) %>% 
    dplyr::select(`study` = study_select,
                  metric,
                  extid,
                  `Participant Age`,
                  `FA ID`,
                  `Worker ID`,
                  `ICF Issue Age` = metric_aging,
                  instanceID,
                  SubmissionDate,
                  status,
                  visit)

element_id <- "icf_detail_table"
tbl <- reactable(
  data,
  columns = list(
    study = colDef(minWidth = 150),
    metric = colDef(minWidth = 350),
    `Participant Age` = colDef(format = colFormat(digits = 1))
  ),
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = TRUE,
  filterable = TRUE,
  elementId = element_id,
  groupBy = c('study', 'metric')
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-icf_metric_detail.csv'))
```

## ICF Status by Roster

This section will show all user with copy of ICF to fill (`ind_icf_completed == 1`) with corresponding verification and resolution status

```{r}
element_id <- "roster_icf_detail_table"
data <- roster %>% 
  dplyr::select(extid, 
                study = study_select, 
               `Participant Age` = age,
               `FA ID` = fa_id) %>% 
    dplyr::left_join(icf_hist %>% 
                         dplyr::select(extid, 
                                       `Worker ID` = cl_id,
                                       `ICF Status` = icf_stat, 
                                       study = study_select), 
                     by = c('extid', 'study')) %>%
    dplyr::mutate(`ICF Status` = tidyr::replace_na(`ICF Status`, 'Unverified'))

tbl <- reactable(
  data,
  columns = list(
    study = colDef(minWidth = 150),
    `Participant Age` = colDef(format = colFormat(digits = 1))
  ),
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = TRUE,
  filterable = TRUE,
  elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-icf_roster_detail.csv'))
```
