---
title: "Bohemia Reports Catalog"
description: |
  Catalog of all Bohemia BI Reports and how to get there
date: "`r Sys.time()`"
output:
  html_document:
    theme: cerulean
    toc: yes
---

### Overview
This is the Catalog of all Bohemia BI Reports and their respective URLs. Reports are categorized into different topics, to drill down to a certain topic, please expand the `topic` column. Each topic will contain different reports with corresponding report URL and ODK URL (Monitoring)

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tools)
```

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri('../../asset/bohemia.jpg'), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:200px; height:100px')
```

```{r}
# variables / creds for ento
env_pipeline_stage <- Sys.getenv("PIPELINE_STAGE")
bucket_source <- 'databrew.org'
bucket_lake_db <- 'bohemia-reporting'
prod_cloudfront_url <- 'https://d27fg4iv55pk9u.cloudfront.net'
cra_url_access <- 'https://databrew.org/-/single/5M6LxeNOWaQaN16yS3ogBwHCscYMY6Q?st=X2LIvoLTAALVcZXzEKNXvSJcURAaC23smaqRNzWOqQY1AguC1qlLP8yNPwVJHb18'
site_url_access <- 'https://databrew.org/-/single/D9ov8lUub0z7qSQcvh0UnvsdQp0RZ9f?st=zzJvtpFqy6yVYtjWRxBhDpIlAlmOhdYBIFODslI8jI3Zx0kHygHHZV3LZ9cSTrVU'
```


```{r}
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = env_pipeline_stage)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```
```{r}
data <- cloudbrewr::aws_s3_get_catalog(bucket = bucket_lake_db) %>%
  dplyr::mutate(url_key = glue::glue('{prod_cloudfront_url}/{key}')) %>%
  dplyr::select(-etag) %>%
  dplyr::mutate(report_name = basename(key)) %>%
    dplyr::mutate(key_split = stringr::str_split(key, "/")) %>% 
    dplyr::rowwise() %>% 
    dplyr::mutate(folder = key_split[1]) %>% 
    dplyr::filter(key != 'index.html',
                  size > 0) %>%
    dplyr::select(topic = folder, 
                  report_name, 
                  size, 
                  last_modified, 
                  url_key, 
                  folder)
```

### Bohemia Data-Ops Reports

This is all reports used in Bohemia Data-Ops team, all reports are updated **hourly 9-5PM EAT and once at 12AM EAT**

```{r}
d <- data %>% dplyr::filter(topic != 'monitoring')
reactable(
    d,
    columns = list(
        topic = colDef(name = 'Topic', minWidth = 200, filterable = TRUE),
        report_name = colDef(name = 'Report Name', minWidth = 300, filterable =TRUE),
        size = colDef(name = "Size (kb)"),
        last_modified = colDef(name = 'Last Modified', minWidth = 200),
        url_key = colDef(name = 'Report URL',
                         cell = function(value, index) {
                           url <- sprintf("%s", 
                                          d[index, "url_key"], value)
                           htmltools::tags$a(href = url, target = "_blank", 'URL')
                        })
    ),
    groupBy = "topic",
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE)
```
