---
title: "Anomalies Reports"
output:
  html_document:
    toc: true
    theme: cerulean
date: '`r Sys.time()`'
---


**Notes**

- Report is refreshed hourly 9-5pm EAT, once 12AM EAT (Please refer to timestamp above)
- Please reach out to [Aryton Tediarjo](atediarjo@gmail.com) via Slack for bug found in this report
- To resolve anomalies please refer to this [Google Sheets Resolution Sheet](https://docs.google.com/spreadsheets/d/1i98uVuSj3qETbrH7beC8BkFmKV80rcImGobBvUGuqbU/edit#gid=0)

**Changelog**

- 2023/07/17: change from less than 10 to less than 4 mins data collection time per this [thread](https://bohemiakenya.slack.com/archives/C042KSRLYUA/p1689599637156259?thread_ts=1689579002.400869&cid=C042KSRLYUA)


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
```

```{r}
# variables / creds
env_pipeline_stage <- Sys.getenv("PIPELINE_STAGE")
Sys.setenv(R_CONFIG_ACTIVE=env_pipeline_stage)
ROLE_NAME <- 'cloudbrewr-aws-role'

# create connection to AWS
tryCatch({
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = ROLE_NAME,
    profile_name =  ROLE_NAME,
    pipeline_stage = env_pipeline_stage)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```


```{r}

anomalies <- cloudbrewr::aws_s3_get_table(
  bucket = 'bohemia-lake-db',
  key = 'bohemia_prod/fact_anomalies/fact_anomalies.csv'
)

```

```{r}
# read in historical table
cloudbrewr::aws_s3_bulk_get(
    bucket = 'bohemia-lake-db',
    prefix = '/bohemia_prod/summary_anomalies_history',
    output_dir = 'data/summary_anomalies_history'
)

tbl <- tibble(file_path = list.files(path = 'data',recursive = TRUE,full.names = TRUE)) %>% 
    dplyr::mutate(comb = stringr::str_split(file_path, '/|=')) %>% 
    dplyr::rowwise() %>% 
    dplyr::mutate(snapshot_date = comb[5]) %>% 
    dplyr::rowwise() %>%
    dplyr::mutate(data = purrr::map(file_path, fread)) %>% 
    dplyr::filter(!is.na(snapshot_date))


anomalies_history <- tbl$data %>% purrr::reduce(dplyr::bind_rows)  %>% 
    dplyr::mutate(snapshot_date = lubridate::date(snapshot_date))
```


```{r, echo = FALSE, message=FALSE}
wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
  tagList(
    tags$button(
      tagList(fontawesome::fa("download"), "Download as CSV"),
      onclick = onclick_command),
    reactable_obj
  ))
}
```

### Historical Anomalies
```{r, fig.height = 3, fig.width = 10}
anomalies_history_grp <- anomalies_history %>%
    dplyr::group_by(snapshot_date) %>% 
    dplyr::summarise(anomalies_count = sum(anomalies_count))

p1 <- anomalies_history_grp %>% 
  ggplot(aes(x = snapshot_date, y = anomalies_count)) +
  geom_line(size = 1) +
  theme_minimal() +
  labs(x = '', y = '')

p2 <- anomalies_history %>%
    ggplot(aes(x = snapshot_date, y = anomalies_count, fill = anomalies_id)) +
    geom_col(width = 0.4) +
    theme_minimal() +
    scale_fill_brewer(palette="Paired") +
    labs(x = '', y = '')

ggplotly(p1)
ggplotly(p2)
```


### Anomalies by Group
```{r}
element_id <- 'anomalies_list_grouped'
tbl <- reactable(
  anomalies %>% 
    dplyr::select(form_id, anomalies_id, KEY),
  groupBy = c("form_id", "anomalies_id"),
  columns = list(
    form_id = colDef(
      name = 'form_id',
      filterable = TRUE
    ),
    anomalies_id = colDef(
      name = 'anomalies_id',
      filterable = TRUE
    ),
    `KEY` = colDef(
      name = 'anomalies_count',
      aggregate = "count")
  ),
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = TRUE,
  wrap = TRUE,
  elementId = element_id
)

wrap_download(tbl, 
              element_id, 
              'anomalies_list_grouped.csv')
```


### Anomalies List Raw
```{r}
element_id <- 'anomalies_list_raw'
tbl <- reactable(
  anomalies,
  columns = list(
    `KEY` = colDef(name = 'KEY', filterable = TRUE),
    form_id = colDef(name = "form_id", filterable = TRUE),
    anomalies_id = colDef(name = "anomalies_id", filterable = TRUE),
    anomalies_description = colDef(name = "anomalies_description")
  ),
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = TRUE,
  wrap = TRUE,
  elementId = element_id
)

wrap_download(tbl, 
              element_id, 
              'anomalies_list_raw.csv')

```

