---
title: "ICF Monitoring Report"
description: |
  ICF Reporting used to track Issues for Monitoring
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(formattable)
library(lubridate)
library(tools)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
REPORTING_BUCKET_NAME <- 'bohemia-reporting-icf-monitoring'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
MIN_DATE <- lubridate::date('2023-11-05')
```


```{r}
INPUT_KEY <- 
  list(
    craremotemonitoring = glue::glue('kwale/raw-form/craremotemonitoring/craremotemonitoring.csv'),
    siteremotemonitoring = glue::glue('kwale/raw-form/siteremotemonitoring/siteremotemonitoring.csv')
  )


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}

create_snapshot_tbl <- function(data){
  min_date <- lubridate::floor_date(
    (data$SubmissionDate %>% lubridate::date() %>% min()),
    unit = 'weeks'
  )
  max_date <- lubridate::floor_date(
    lubridate::today(),
    unit = 'weeks'
  )
  date_list <- seq.Date(min_date, max_date, "weeks")
  data_hist <- purrr::map_dfr(date_list, function(d){
    data %>% 
      dplyr::mutate(run_date = d) %>% 
      dplyr::filter(SubmissionDate <= d)
  })
  
  return(data_hist)
}

pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

#' @description clean column names
#' @param data dataset to clean
clean_column_names <- function(data){
  names(data) <- unlist(lapply(strsplit(names(data), '-'), function(a){a[length(a)]}))
  return(data)
}
```



```{r}
siteremotemonitoring <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = INPUT_KEY$siteremotemonitoring
) %>% clean_column_names() %>% 
  dplyr::filter(stringr::str_detect(report_id, 'ICF'))
```


```{r}
site_url_access <- 'https://databrew.org/-/single/D9ov8lUub0z7qSQcvh0UnvsdQp0RZ9f?st=zzJvtpFqy6yVYtjWRxBhDpIlAlmOhdYBIFODslI8jI3Zx0kHygHHZV3LZ9cSTrVU'

site_resolve_link <- '{site_url_access}&d%5B/data/group_indentifier/report_id%5D={report_id}&d%5B/data/group_indentifier/issue_type%5D=Resolve&d%5B/data/group_resolve/issue_id%5D={instanceID}'

prod_cloudfront_url <- 'https://d3uelmvt33f8hw.cloudfront.net'
```


## ICF Monitoring Reports

This catalog covers all reports for CRA monitoring. **Reports are refreshed every Sunday 12.00AM EAT**, each report will be snapshotted into a corresponding report ID where user will be able to point to a specific ID for review. Please drill-down to check all the report snapshots


#### Guideline:

1. Expand drop-down in the interactive table by clicking on the `Topic` field in the table

2. To check on the reports, click the URL under `Report URL`

3. To provide monitoring review, click the URL under `CRA Review URL` and `Site Review URL` depending on user. Clicking the URL will pre-fill forms with corresponding `Report ID` to report findings

```{r}
data <- cloudbrewr::aws_s3_get_catalog(bucket = REPORTING_BUCKET_NAME) %>% 
    dplyr::filter(stringr::str_detect(key, 'report/')) %>% 
    dplyr::filter(stringr::str_detect(key, 'html')) %>% 
    dplyr::mutate(grp = dirname(key)) %>% 
  dplyr::mutate(url_key = glue::glue('{prod_cloudfront_url}/{key}')) %>%
  dplyr::select(-etag) %>%
  dplyr::mutate(report_name = basename(key)) %>%
    dplyr::mutate(key_split = stringr::str_split(key, "/")) %>% 
    dplyr::rowwise() %>% 
    dplyr::mutate(folder = key_split[2]) %>% 
    dplyr::filter(key != 'index.html',
                  size > 0) %>%
    dplyr::select(report_name, 
                  size, 
                  last_modified, 
                  url_key, 
                  topic = folder) %>%
    dplyr::ungroup() %>% 
    dplyr::mutate(
      site_url_key = glue::glue(
        '{site_url_access}&d%5B/data/group_indentifier/report_id%5D={report_id}&d%5B/data/group_indentifier/issue_type%5D=Open',
        url_access = url_access,
        report_id = file_path_sans_ext(basename(report_name)))
  )
```

```{r}
reactable(
    data %>% dplyr::select(-topic),
    columns = list(
        report_name = colDef(name = 'Report Name', minWidth = 200, filterable =TRUE),
        size = colDef(name = "Size (kb)"),
        last_modified = colDef(name = 'Last Modified', minWidth = 200),
        url_key = colDef(name = 'Report URL',
                         cell = function(value, index) {
                           url <- sprintf("%s", 
                                          data[index, "url_key"], value)
                           htmltools::tags$a(href = url, target = "_blank", 'URL')
                        }),
        site_url_key = colDef(name = 'Site Review URL',
                         cell = function(value, index) {
                           url <- sprintf("%s", 
                                          data[index, "site_url_key"], value)
                           htmltools::tags$a(href = url, target = "_blank", 'URL')
                        })
    ),
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE)
```


## ICF Site Monitoring Open Issues

```{r}
resolved_issue <- siteremotemonitoring %>% 
    dplyr::filter(issue_type == 'Resolve') %>% 
    dplyr::arrange(desc(SubmissionDate)) %>%
    dplyr::distinct(issue_id) %>%
    dplyr::pull(issue_id)


tbl <- siteremotemonitoring %>% 
    dplyr::filter(issue_type == 'Open', 
                  !instanceID %in% resolved_issue) %>% 
    dplyr::mutate(resolve_link = glue::glue(site_resolve_link)) %>%
    dplyr::select(SubmissionDate, 
                  `Issue ID` = instanceID,
                  `Report ID` = report_id, 
                  resolve_link,
                  issue,
                  `Affect Participant Safety` = affect_participant_safety,
                  `Affected Participant ID` = affected_participant_id)


element_id <- 'site_monitoring_open_issues'
tbl <- reactable(
        tbl,
        columns = list(
                  SubmissionDate = colDef(
                    name = 'SubmissionDate',
                    minWidth = 200
                  ),
                  `Issue ID` = colDef(
                    name = 'Issue ID',
                    minWidth = 200
                  ),
                  `Report ID` = colDef(
                    name = 'Report ID',
                    minWidth = 200
                  ),
                  resolve_link = colDef(name = 'Resolve Link',
                         cell = function(value, index) {
                           url <- sprintf("%s", 
                                          tbl[index, "resolve_link"], value)
                           htmltools::tags$a(href = url, target = "_blank", 'URL')
                        })
        ),
        highlight = TRUE,
        resizable = TRUE,
        bordered = TRUE,
        striped = TRUE,
        filterable =TRUE,
        elementId = element_id)

wrap_download(tbl,  
              element_id,
              'site_monitoring_open_issues.csv')
```

## ICF Site Monitoring Closed Issues

```{r}
tbl <- siteremotemonitoring %>% 
    dplyr::filter(issue_type == 'Resolve', issue_id %in% resolved_issue) %>% 
    dplyr::select(SubmissionDate, 
                  `Issue ID` = issue_id,
                  `Report ID` = report_id,
                  issue,
                  `Affect Participant Safety` = affect_participant_safety,
                  `Reviewer Name` = resolver_name,
                  `Team Members Informed` = team_members_informed,
                  `Actions Taken` = actions_taken)


element_id <- 'cra_closed_issues'
tbl <- reactable(
        tbl,
        highlight = TRUE,
        resizable = TRUE,
        bordered = TRUE,
        striped = TRUE,
        filterable =TRUE,
        elementId = element_id)

wrap_download(tbl,  
              element_id,
              'cra_closed_issues.csv')
```

