---
description: |
  Reporting used to track ICF in SE & PK
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

#### Description:

This report is used for ICF monitoring based on this [Reporting Document](https://docs.google.com/document/d/1WvrQ7EDnFFL87iL5reFgKC6dGWA5EEzgma-gLuSZWKQ/edit#heading=h.qmggsikczir8)

#### Refresh Rate:

**This report will be updated every Monday 12AM EAT**

#### Bug Reports:

Please report bug to `e.elobolobo@gmail.com` / `atediarjo@gmail.com`

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(formattable)
library(DBI)
library(noctua)
library(lubridate)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
```


```{r}
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})


if(Sys.getenv('PIPELINE_STAGE') != 'production'){
  BUCKET_TARGET <- 's3://develop-athena-query-results/'
}else{
  BUCKET_TARGET <- 's3://bohemia-athena-query-results/'
}

con <- dbConnect(noctua::athena(),
               s3_staging_dir=BUCKET_TARGET,
               region_name='us-east-1')

```

```{r}
wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}
```


```{r}
# retrieve from athena
version <- format(floor_date(lubridate::today(), 'week'), "%Y%m%d")
sql_query <- "
-- unresolved ICF
select
	cast(run_date as date) as run_date,
	'Safety ICF Unresolved' as metric,
	'Safety ICF' as source,
	extid,
	date_diff(
              'day',
	cast(safety_verification_date as date),
	cast(run_date as date)) age
from
	metadata.icf_hist
where
	safety_icf_status = 'Rectification'

union all 

select
	cast(run_date as date) as run_date,
	'Efficacy ICF Unresolved' as metric,
	'Efficacy ICF' as source,
	extid,
	date_diff(
              'day',
	cast(efficacy_verification_date as date),
	cast(run_date as date)) age
from
	metadata.icf_hist
where
	efficacy_icf_status = 'Rectification'
	and efficacy_status is not null
	
union all

-- unverified icf 
select
	cast(run_date as date) as run_date,
	'Safety ICF Unverified' as metric,
	'Safety ICF' as source,
	extid,
	date_diff(
              'day',
	cast(safety_date as date),
	cast(run_date as date)) age
from
	metadata.icf_hist
where
	safety_icf_status is null
	and safety_date is not null

union all 
  
select
	cast(run_date as date) as run_date,
	'Efficacy ICF Unverified' as metric,
	'Efficacy ICF' as source,
	extid,
	date_diff(
              'day',
	cast(efficacy_date as date),
	cast(run_date as date)) age
from
	metadata.icf_hist
where
	efficacy_icf_status is null
	and efficacy_status is not null
	and efficacy_date is not null

union all

-- missing icf 
select
	cast(run_date as date) as run_date,
	'Safety ICF Missing' as metric,
	'Safety ICF' as source,
	extid,
	date_diff(
              'day',
	cast(safety_date as date),
	cast(run_date as date)
          ) as age
from
	metadata.icf_hist
where
	safety_icf_status = 'Lost-Not Found'

union all 

select
	cast(run_date as date) as run_date,
	'Efficacy ICF Missing' as metric,
	'Efficacy ICF' as source,
	extid,
	date_diff(
              'day',
	cast(efficacy_date as date),
	cast(run_date as date)
          ) as age
from
	metadata.icf_hist
where
	efficacy_icf_status = 'Lost-Not Found'
	and efficacy_status is not null
"


d <- tbl(con, sql(sql_query)) %>% collect() 

```


---
title: "ICF-`r version` Monitoring ICF Reports"
---

## ICF Monitoring Weekly Trends

Click on the legend to focus on a desired metric

```{r}
w_data <- d %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(week_start == run_date) %>% 
    dplyr::mutate(age = as.numeric(age))
c_data <- w_data %>%
    dplyr::filter(run_date == max(.$run_date)) %>% 
    dplyr::mutate(age = as.numeric(age))
```

### Overall ICF Trends

```{r, fig.width=10, fig.height=3}
p <-w_data %>% 
    dplyr::group_by(run_date, metric) %>% 
    dplyr::summarise(`overall` = n_distinct(extid),
                     `20 days aging` = n_distinct(extid[age>20])) %>%
    dplyr::mutate(value = as.numeric(overall)) %>%
    ggplot(aes(x = run_date, y = value, color = metric)) +
    geom_line() +
    geom_point() +
    labs(x = "", y = "") +
    theme_minimal()


ggplotly(p)
```
### ICF Trends (20 days aging)
```{r, fig.width=10, fig.height=3}
p <-w_data %>% 
    dplyr::group_by(run_date, metric) %>% 
    dplyr::summarise(`overall` = n_distinct(extid),
                     `20 days aging` = n_distinct(extid[age>20])) %>%
    dplyr::mutate(value = as.numeric(`20 days aging`)) %>%
    ggplot(aes(x = run_date, y = value, color = metric)) +
    geom_line() +
    geom_point() +
    labs(x = "", y = "") +
    theme_minimal()


ggplotly(p)
```


## Current Week ICF Monitoring Summary
```{r}
data <- c_data %>% 
    dplyr::group_by(metric) %>% 
    dplyr::summarise(`Overall` = n_distinct(extid),
                     `20 days aging` = n_distinct(extid[age>20]))

reactable(data)
```


## ICF Details Table
This is the interactive detail table that creates the plot and the summary table above. There are several actions you can take with this table:

#### 1. Filtering:

*source*:

- `Safety ICF`

- `Efficacy ICF`

*metric*:

- `Efficacy ICF Unresolved`

- `Safety ICF Unresolved` 

- `Safety ICF Unverified`   

- `Efficacy ICF Unverified`

#### 2. Sorting:

Please press on the column

#### 3. Downloading:

Please press the download button

```{r}
data <- c_data %>% 
    dplyr::select(-week_start, -run_date) %>% 
    dplyr::select(source,metric,extid, icf_age = age)

element_id <- "icf_detail_table"
tbl <- reactable(data, 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-icf_monitoring_detail.csv'))
```

