---
description: |
  Reporting used to track Lab Monitoring
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

#### Description:

This report is used for Lab monitoring based on this [Reporting Document](https://docs.google.com/document/d/1WvrQ7EDnFFL87iL5reFgKC6dGWA5EEzgma-gLuSZWKQ/edit#heading=h.qmggsikczir8)

#### Refresh Rate:

**This report will be updated every Monday 12AM EAT**

#### Bug Reports:

Please report bug to `e.elobolobo@gmail.com` / `atediarjo@gmail.com`

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tidyr)
library(lubridate)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
MIN_DATE <- lubridate::date('2023-11-05')
```

```{r}
tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```

```{r}
pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}
```

```{r}
INPUT_KEY <- list(
    v0 = glue::glue('{SE_FOLDER_TARGET}/v0demography/v0demography.csv'),
    v0_repeat = glue::glue('{SE_FOLDER_TARGET}/v0demography/v0demography-repeat_individual.csv'),
    sepk_icf_verification = glue::glue('{SE_FOLDER_TARGET}/sepk_icf_verification/sepk_icf_verification.csv'),
    # sepk_icf_resolution =  glue::glue('{SE_FOLDER_TARGET}/sepk_icf_resolution/sepk_icf_resolution.csv'),
    safety = glue::glue('{SE_FOLDER_TARGET}/safety/safety.csv'),
    safetynew = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew.csv'),
    safety_repeat_individual = glue::glue('{SE_FOLDER_TARGET}/safety/safety-repeat_individual.csv'),
    safetynew_repeat_individual = glue::glue('{SE_FOLDER_TARGET}/safetynew/safetynew-repeat_individual.csv'),
    efficacy =  glue::glue('{SE_FOLDER_TARGET}/efficacy/efficacy.csv')
  )


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})
```


```{r}
#################################
# Fetch v0 demography
#################################
# pk <- cloudbrewr::aws_s3_get_table(
#   bucket = 'databrew.org',
#   key = 'kwale/clean-form/pk/pk.csv'
# ) %>%
#   pad_hhid()

efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/efficacy/efficacy.csv'
) %>%
  pad_hhid()

sepk_icf_verification <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = INPUT_KEY$sepk_icf_verification
) %>%
  pad_hhid() 

lab <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/lab/lab.csv'
) %>%
  pad_hhid() %>% 
  dplyr::group_by(sample, sample_status) %>%
  dplyr::mutate(max_submission_date = max(SubmissionDate)) %>%
  dplyr::filter(SubmissionDate == max_submission_date)  %>%
  dplyr::mutate(incidences = case_when(
        sample_status == 'Approved' ~ 
            coalesce(match_tracking_incidence_select2, match_tracking_incidence_select),
        sample_status == 'Pending' ~ 
            coalesce(pending_incidence_select, 
                     coalesce(match_tracking_incidence_select2, match_tracking_incidence_select)),
        sample_status == "Quarantine" ~ 
            coalesce(quarantine_incidence_select, 
                     coalesce(match_tracking_incidence_select2, match_tracking_incidence_select)))) 

lab2 <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/lab2/lab2.csv'
) %>%
  pad_hhid()

lab_metadata_zp <- cloudbrewr::aws_s3_get_object(
  bucket = 'databrew.org',
  key = 'metadata/lab_metadata.zip'
) 


lab1_incidences_mapping <- lab %>% 
    dplyr::select(sample, 
                  study,
                  instanceID,
                  SubmissionDate,
                  sample_status,
                  match_tracking_incidence_select, 
                  match_tracking_incidence_select2,
                  pending_incidence_select,
                  quarantine_incidence_select,
                  extid) %>% 
    dplyr::mutate(across(where(is.character), ~na_if(., ""))) %>% 
    dplyr::mutate(across(where(is.character), ~na_if(., "none"))) %>%
    dplyr::mutate(incidences = case_when(
        sample_status == 'Approved' ~ 
            coalesce(match_tracking_incidence_select2, match_tracking_incidence_select),
        sample_status == 'Pending' ~ 
            coalesce(pending_incidence_select, 
                     coalesce(match_tracking_incidence_select2, match_tracking_incidence_select)),
        sample_status == "Quarantine" ~ 
            coalesce(quarantine_incidence_select, 
                     coalesce(match_tracking_incidence_select2, match_tracking_incidence_select))
    )) %>% 
    dplyr::select(extid, instanceID, SubmissionDate, sample, sample_status, incidences, study) %>% 
    dplyr::mutate(source = 'lab')


lab2_incidences_mapping <- lab2 %>% 
    dplyr::select(
      sample, 
      study,
      instanceID,
      SubmissionDate,
      sample_status,
      quarantine_incidence_select,
      extid) %>% 
    dplyr::mutate(across(where(is.character), ~na_if(., ""))) %>% 
    dplyr::mutate(across(where(is.character), ~na_if(., "none"))) %>%
    dplyr::mutate(incidences = case_when(
      sample_status == "Quarantine" ~ quarantine_incidence_select, TRUE ~ NA_character_
    )) %>% 
    dplyr::select(extid, instanceID, SubmissionDate, sample, sample_status, incidences, study) %>% 
    dplyr::mutate(source = 'lab2')

```

```{r}
version <- format(floor_date(lubridate::today(), 'week'), "%Y%m%d")

mapping <- dplyr::tribble(
  ~incidences, ~incidences_long,
  'date_unavailable',	'Data not available',
  'samples_not_dry',	'Samples not dry',
  'dbs_incomplete',	'DBS incomplete',
  'participant_issue',	'Participant not preselected or wrong age',
  'tracking_issue',	'Sample not in the tracking form',
  'data_mismatch',	'Data don’t match',
  'icf_status',	'ICF Status: Unresolved/Lost Not-Found',
  'other',	'Other'
)

incidences_mapping <- dplyr::bind_rows(lab1_incidences_mapping,lab2_incidences_mapping) %>% 
    dplyr::ungroup() %>% 
    dplyr::rowwise() %>%
    dplyr::mutate(incidences = stringr::str_split(incidences, pattern=" ")) %>% 
    tidyr::unnest(incidences) %>% 
    dplyr::ungroup() %>% 
    dplyr::left_join(mapping) %>% 
    dplyr::mutate(incidences = incidences_long) 
```

---
title: "LAB-`r version` Monitoring Lab Reports"
---

```{r}
# create snapshot table
min_date <- lab$SubmissionDate %>% lubridate::date() %>% min()
max_date <- lubridate::today()
date_list <- seq.Date(min_date, max_date, "days")

lab_hist <- purrr::map_dfr(date_list, function(d){
  incidences_mapping %>% 
    dplyr::mutate(run_date = d) %>% 
    dplyr::filter(SubmissionDate <= d)
})

grouped_lab_hist <- lab_hist %>% 
    dplyr::group_by(run_date) %>% 
    dplyr::summarise(samples = list(sample))

# create snapshot table for efficacy
min_date <- efficacy$SubmissionDate %>% lubridate::date() %>% min()
max_date <- lubridate::today()
date_list <- seq.Date(min_date, max_date, "days")
eff_hist <- purrr::map_dfr(date_list, function(d){
  efficacy %>% 
    dplyr::mutate(run_date = d) %>% 
    dplyr::filter(SubmissionDate <= d)
  }) %>% 
  dplyr::select(instanceID, run_date, sample = dbs_barcode, SubmissionDate, extid) %>% 
  dplyr::filter(sample != "") %>% 
  dplyr::distinct()



samples_in_eff_by_run <- eff_hist %>%
    dplyr::anti_join(lab_hist, 
                     by = c('run_date', 'sample')) %>% 
  dplyr::filter(run_date >= MIN_DATE)
samples_in_lab_by_run <- lab_hist %>%
    dplyr::anti_join(samples_in_eff_by_run,
                     by = c('run_date', 'sample')) %>% 
  dplyr::filter(run_date >= MIN_DATE)
```

### a). Pending – samples pending for >10 days
```{r}
from_lab <- samples_in_lab_by_run %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days"))) %>% 
    dplyr::group_by(run_date) %>% 
    dplyr::summarise(
      `Pending Samples` = n_distinct(sample[sample_status == 'Pending']),
      `Pending Samples for more than 10 days` = n_distinct(sample[age>10 & sample_status == 'Pending']))

tbl <- from_lab

reactable(tbl)
```

```{r}
from_lab <- samples_in_lab_by_run %>% 
    dplyr::filter(run_date == floor_date(lubridate::today(), 'week')) %>%
    dplyr::ungroup() %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days"))) %>% 
    dplyr::select(-week_start) %>% 
    dplyr::filter(sample_status == 'Pending') %>% 
    dplyr::select(run_date, source, 
                  instanceID, 
                  sample,
                  `Sample Status` = sample_status, 
                  SubmissionDate, 
                  extid, 
                  incidences,
                  age)


tbl <- dplyr::bind_rows(from_lab)

element_id <- 'pending_samples.csv'
tbl <- reactable(tbl, 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-pending_lab_samples_detail.csv'))
```



### b). Quarantined samples – anomaly report for each scenario:
```{r}
from_lab <- samples_in_lab_by_run %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days"))) %>% 
    dplyr::group_by(run_date) %>% 
    dplyr::summarise(`Quarantine` = n_distinct(sample[sample_status == 'Quarantine']))

tbl <- from_lab

reactable(tbl)
```


```{r}
from_lab <- samples_in_lab_by_run %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == floor_date(lubridate::today(), 'week')) %>%
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days"))) %>% 
    dplyr::select(-week_start) %>% 
    dplyr::select(instanceID, source, sample_status, run_date, sample, SubmissionDate, extid, age, incidences) %>% 
    dplyr::filter(sample_status == 'Quarantine')  %>% 
    dplyr::select(run_date, source, 
                  instanceID, 
                  sample,
                  `Sample Status` = sample_status, 
                  SubmissionDate, 
                  extid, 
                  incidences,
                  age)



tbl <- dplyr::bind_rows(from_lab)

element_id <- 'quarantined_samples.csv'
tbl <- reactable(tbl, 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-quarantined_lab_samples_detail.csv'))
```


### c). Missing Samples
```{r}
from_field <- samples_in_eff_by_run %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days"))) %>% 
    dplyr::group_by(run_date) %>% 
    dplyr::summarise(
      `Missing Samples` = n_distinct(sample),
      `Missing Samples 0-10 days` = n_distinct(sample[age<=10]),
      `Missing Samples 10-20 days` = n_distinct(sample[age>10 & age<=20]),
      `Missing Samples >20 days` = n_distinct(sample[age>20]))



tbl <- from_field

reactable(tbl)
```

```{r}
from_field <- samples_in_eff_by_run %>% 
    dplyr::mutate(week_start = lubridate::floor_date(run_date, "week")) %>% 
    dplyr::filter(run_date == floor_date(lubridate::today(), 'week')) %>%
    dplyr::filter(run_date == week_start) %>%
    dplyr::mutate(age = as.numeric(difftime(lubridate::date(run_date), 
                                            lubridate::date(SubmissionDate), units = "days")),
                  source = 'Field (efficacy)') %>% 
    dplyr::select(-week_start) %>% 
    dplyr::select(run_date, source, 
                  instanceID, 
                  sample,
                  SubmissionDate, 
                  extid, 
                  age)

tbl <- dplyr::bind_rows(from_field)

element_id <- 'missing_samples.csv'
tbl <- reactable(tbl, 
    highlight = TRUE,
    resizable = TRUE,
    bordered = TRUE,
    striped = TRUE,
    filterable = TRUE,
    elementId = element_id
)

wrap_download(
  tbl, 
  element_id,
  glue::glue('{version}-missing_lab_samples_detail.csv'))
```


