---
description: |
  Reporting used to track Pharmacy Monitoring
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: cerulean
  pdf_document:
    toc: yes
---

#### Description:

This report is used for Pharmacy monitoring based on this [Reporting Document](https://docs.google.com/document/d/1WvrQ7EDnFFL87iL5reFgKC6dGWA5EEzgma-gLuSZWKQ/edit#heading=h.qmggsikczir8)

#### Refresh Rate:

**This report will be updated every Monday 12AM EAT**

#### Bug Reports:

Please report bug to `e.elobolobo@gmail.com` / `atediarjo@gmail.com`


#### Definitions:

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  comment = '', 
  echo = FALSE,
  message = FALSE,
  cache=FALSE,
  warning=FALSE
)
```

```{r, echo=FALSE, message=FALSE}
library(reactable)
library(data.table)
library(dplyr)
library(htmltools)
library(glue)
library(fontawesome)
library(ggplot2)
library(plotly)
library(tidyr)
library(lubridate)
```

```{r}
# STATIC VARIABLES FOR I/O
ENV_PIPELINE_STAGE <- Sys.getenv("PIPELINE_STAGE")
DATA_STAGING_BUCKET_NAME <- 'databrew.org'
DATA_LAKE_BUCKET_NAME <- 'bohemia-lake-db'
PROJECT_SOURCE <- 'kwale'
SE_FOLDER_TARGET <- glue::glue('{PROJECT_SOURCE}/clean-form')
MIN_DATE <- lubridate::date('2023-11-05')
```


```{r}
INPUT_KEY <- list(
  sepk_icf_verification = glue::glue('{DATA_STAGING_BUCKET_NAME}/sepk_icf_verification/sepk_icf_verification.csv'),
  sepk_icf_resolution =  glue::glue('{DATA_STAGING_BUCKET_NAME}/sepk_icf_resolution/sepk_icf_resolution.csv'),
  safety = glue::glue('{DATA_STAGING_BUCKET_NAME}/safety/safety.csv'),
  safetynew = glue::glue('{DATA_STAGING_BUCKET_NAME}/safetynew/safetynew.csv'),
  efficacy =  glue::glue('{DATA_STAGING_BUCKET_NAME}/efficacy/efficacy.csv'),
  pkday0 =  glue::glue('{DATA_STAGING_BUCKET_NAME}/pkday0/pkday0.csv')
)


tryCatch({
  logger::log_info('Attempt AWS login')
  # login to AWS - this will be bypassed if executed in CI/CD environment
  cloudbrewr::aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name =  'cloudbrewr-aws-role',
    pipeline_stage = ENV_PIPELINE_STAGE)

}, error = function(e){
  logger::log_error('AWS Login Failed')
  stop(e$message)
})

```

```{r}
pad_hhid <- function(data){
  if('hhid' %in% names(data)){
    data %>%
      dplyr::mutate(hhid = stringr::str_pad(hhid, 5, pad = "0"))
  }else{
    data
  }
}

wrap_download <- function(reactable_obj, element_id, output_filename){
  onclick_command <- glue::glue(
    "Reactable.downloadDataCSV('{element_id}', '{output_filename}')")
  htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = onclick_command),
      reactable_obj
    ))
}

create_snapshot_tbl <- function(data){
  min_date <- lubridate::floor_date(
    (data$SubmissionDate %>% lubridate::date() %>% min()),
    unit = 'weeks'
  )
  max_date <- lubridate::floor_date(
    lubridate::today(),
    unit = 'weeks'
  )
  date_list <- seq.Date(min_date, max_date, "weeks")
  data_hist <- purrr::map_dfr(date_list, function(d){
    data %>% 
      dplyr::mutate(run_date = d) %>% 
      dplyr::filter(SubmissionDate <= d)
  })
  
  return(data_hist)
}
```


```{r}
#################################
# Fetch v0 demography
#################################
pharmacy_fa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_fa/pharmacy_fa.csv'
) %>%
  pad_hhid()
pharmacy_sfa <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy_sfa/pharmacy_sfa.csv'
) %>%
  pad_hhid() 
pharmacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/pharmacy/pharmacy.csv'
) %>%
  pad_hhid() 

v0_repeat <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = 'kwale/clean-form/v0demography/v0demography-repeat_individual.csv'
) %>%
  pad_hhid() 


efficacy <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/efficacy/efficacy.csv')) %>%
  pad_hhid()

safety <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety.csv')) %>%
  pad_hhid()

safetynew <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew.csv')) %>%
  pad_hhid()

safety_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safety/safety-repeat_individual.csv')) %>%
  pad_hhid()

safetynew_repeat_individual <- cloudbrewr::aws_s3_get_table(
  bucket = 'databrew.org',
  key = glue::glue('{PROJECT_SOURCE}/clean-form/safetynew/safetynew-repeat_individual.csv')) %>%
  pad_hhid()


assignments <- cloudbrewr::aws_s3_get_table(
    bucket = 'bohemia-lake-db',
    key = glue::glue('bohemia_ext_data/assignments/assignments.csv')) %>%
    pad_hhid()



version <- format(floor_date(lubridate::today(), 'week'), "%Y%m%d")
```

---
title: "PHARMACY-`r version` Monitoring Pharmacy Reports"
---


```{r}

safety_merged_tbl <- safety %>% 
    dplyr::inner_join(safety_repeat_individual %>% 
                          dplyr::select(repeat_key = KEY, everything()), by = c('KEY'='PARENT_KEY'))


safetynew_merged_tbl <- safetynew %>% 
    dplyr::inner_join(safetynew_repeat_individual %>% 
                          dplyr::select(repeat_key = KEY, everything()), by = c('KEY'='PARENT_KEY'))


safety_hist <- create_snapshot_tbl(safety_merged_tbl)
safetynew_hist <- create_snapshot_tbl(safetynew_merged_tbl)
efficacy_hist <- create_snapshot_tbl(efficacy)
pharm_hist <- create_snapshot_tbl(pharmacy)
pharm_sfa_hist <- create_snapshot_tbl(pharmacy_sfa)
pharm_fa_hist <- create_snapshot_tbl(pharmacy_fa)
```


```{r}

## pharmacy
pharmacy_list <- list()

# pharmacy initial stock
pharmacy_list$pharmacy_initial_stock <- pharm_hist %>% 
    dplyr::filter(source_entry == 'supplier') %>% 
    dplyr::select(
      run_date,
      alb_tabno, 
      ivm_tabno, 
      coartem80_tabno, 
      coartem20_tabno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols = !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(pharmacy_arrival = sum(value)) 

pharmacy_list$pharmacy_sent_to_sfa <- pharm_hist %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(
      run_date,
      alb_tabno, 
      ivm_tabno, 
      coartem80_tabno, 
      coartem20_tabno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols = !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(pharmacy_dispatch = sum(value)) 

pharmacy_list$pharmacy_unused <- pharm_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'field') %>% 
    dplyr::select(
      run_date,
      starts_with('unused')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>%
    dplyr::summarise(pharmacy_unused_return = sum(value))


pharmacy_list$pharmacy_unusable <- pharm_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'field') %>% 
    dplyr::select(
      run_date,
      starts_with('unusable')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>%
    dplyr::summarise(pharmacy_unusable_return = sum(value))


pharmacy_list$pharmacy_blister <- pharm_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'field') %>% 
    dplyr::select(
      run_date,
      starts_with('blister')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>%
    dplyr::summarise(pharmacy_empty_blister_return = sum(value))

pharmacy_flow_df <- pharmacy_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )


## pharmacy
pharmacy_sfa_list <- list()

# pharmacy initial stock
pharmacy_sfa_list$pharmacy_sfa_initial_stock <- pharm_sfa_hist %>% 
    dplyr::filter(source_entry == 'pharmacy') %>% 
    dplyr::select(
      run_date,
      alb_tabsno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(sfa_arrival = sum(value))


pharmacy_sfa_list$pharmacy_sfa_sent_to_fa <- pharm_sfa_hist %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(
      run_date,
      alb_tabsno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(sfa_dispatch = sum(value))


pharmacy_sfa_list$unused_return <-pharm_sfa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'fa') %>% 
    dplyr::select(
      run_date,
      starts_with('unused')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(sfa_unused_return = sum(value))

pharmacy_sfa_list$unusable_return <-pharm_sfa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'fa') %>% 
    dplyr::select(
      run_date,
      starts_with('unusable')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(sfa_unusable_return = sum(value))


pharmacy_sfa_list$empty_blister_return <- pharm_sfa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'fa') %>% 
    dplyr::select(
      run_date,
      starts_with('blister')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(sfa_empty_blister_return = sum(value))

pharmacy_sfa_flow_df <- pharmacy_sfa_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )



## pharmacy
pharmacy_fa_list <- list()

# pharmacy initial stock
pharmacy_fa_list$initial_stock <- pharm_fa_hist %>% 
    dplyr::filter(source_entry == 'sfa') %>% 
    dplyr::select(
      run_date,
      alb_tabletno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(fa_arrival = sum(value)) 


pharmacy_fa_list$dispatch <- pharm_fa_hist %>% 
    dplyr::filter(operation == 'dispatch') %>% 
    dplyr::select(
      run_date,
      alb_tabletno, 
      ivm_tabletno, 
      coartem80_tabletno, 
      coartem24_tabletno,
      prdt_kitsno) %>%
    tidyr::pivot_longer(cols = !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(fa_dispatch = sum(value))

pharmacy_fa_list$unused_return <- pharm_fa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'cl') %>% 
    dplyr::select(
      run_date,
      starts_with('unused')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(fa_unused_return = sum(value))

pharmacy_fa_list$unusable_return <- pharm_fa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'cl') %>% 
    dplyr::select(
      run_date,
      starts_with('unusable')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(fa_unusable_return = sum(value))


pharmacy_fa_list$empty_blister_return <- pharm_fa_hist %>% 
    dplyr::filter(operation == 'arrival',
                  source_entry == 'cl') %>% 
    dplyr::select(
      run_date,
      starts_with('blisters')) %>%
    tidyr::pivot_longer(cols =  !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    tidyr::drop_na() %>% 
    dplyr::mutate(name = case_when(stringr::str_detect(name, 'ivm') ~ 'ivm',
                                  stringr::str_detect(name, 'alb') ~ 'alb',
                                  stringr::str_detect(name, 'coartem8') ~ 'coartem80',
                                  stringr::str_detect(name, 'coartem2') ~ 'coartem20',
                                  stringr::str_detect(name, 'prdt') ~ 'prdt')) %>%
    dplyr::group_by(run_date, name) %>% 
    dplyr::summarise(fa_empty_blister_return = sum(value))


pharmacy_fa_flow_df <- pharmacy_fa_list %>% 
    purrr::reduce(dplyr::left_join) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    )



cl_list <- list()
cl_list$safety <- safety_hist %>% 
    dplyr::select(
      run_date,
      num_ivermectin_tablets_taken,
      num_ivermectin_tablets_taken_2,
      num_albendzole_pills,
      num_albendzole_pills_2,
      num_extra_albendazole,
      num_extra_albendazole_2,
      num_extra_ivermectin,
      num_extra_ivermectin_2,
      preg_test_result, 
      preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = !run_date) %>% 
    dplyr::mutate(value = tidyr::replace_na(value, 0)) %>%
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    dplyr::group_by(run_date, grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(value))


cl_list$safetynew <- safetynew_hist %>% 
    dplyr::select(
      run_date,
      num_ivermectin_tablets_taken,
      num_ivermectin_tablets_taken_2,
      num_albendzole_pills,
      num_albendzole_pills_2,
      num_extra_albendazole,
      num_extra_albendazole_2,
      num_extra_ivermectin,
      num_extra_ivermectin_2,
      preg_test_result, 
      preg_test_2_result) %>% 
    dplyr::mutate(preg_test_result = case_when(preg_test_result != "" ~ 1, TRUE ~ 0),
                  preg_test_2_result = case_when(preg_test_2_result != "" ~ 1, TRUE ~ 0)) %>% 
    tidyr::pivot_longer(cols = !run_date) %>% 
    mutate(
        across(everything(), ~replace_na(.x, 0))
    ) %>% 
    dplyr::mutate(grp = case_when(stringr::str_detect(name, 'ivermectin') ~ 'ivm',
                                  stringr::str_detect(name, 'albendzole') ~ 'alb',
                                  stringr::str_detect(name, 'albendazole') ~ 'alb',
                                  stringr::str_detect(name, 'preg') ~ 'prdt')) %>% 
    dplyr::group_by(run_date, grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(value))

cl_list$efficacy <- efficacy_hist %>% 
    dplyr::mutate(grp = case_when(have_80_480_coartem != 'yes' ~ 'coartem20',
                                   TRUE ~ 'coartem80')) %>% 
    dplyr::group_by(run_date, grp) %>% 
    dplyr::summarise(coartem = sum(num_coartem_tablets_given, na.rm = T),
                     coartem_ext = sum(num_extra_coartem_tablets_used, na.rm = T)) %>% 
    dplyr::mutate(stock_used_by_cl = coartem + coartem_ext) %>% 
    dplyr::select(run_date, grp, stock_used_by_cl)

stock_used_by_cl <- cl_list %>% 
    purrr::reduce(dplyr::full_join) %>% 
    dplyr::group_by(run_date, grp) %>% 
    dplyr::summarise(stock_used_by_cl = sum(stock_used_by_cl)) %>% 
    dplyr::select(run_date, name = grp, everything())

df <- pharmacy_flow_df %>% 
    dplyr::left_join(pharmacy_sfa_flow_df, by = c('run_date', 'name')) %>% 
    dplyr::left_join(pharmacy_fa_flow_df,  by = c('run_date', 'name')) %>% 
    dplyr::left_join(stock_used_by_cl,  by = c('run_date', 'name')) %>% 
    dplyr::mutate(across(everything(), ~replace_na(.x, 0))) %>% 
    dplyr::ungroup() %>%
    dplyr::filter(run_date >= MIN_DATE)
```

## Pharmacy to SFA Flow Summary
```{r}
tbl <- df %>% 
  dplyr::mutate(pharmacy_stock = (pharmacy_arrival - pharmacy_dispatch) + pharmacy_unused_return) %>% 
  dplyr::select(run_date, 
                name,
                `Pharmacy Arrival` = pharmacy_arrival,
                `Pharmacy Dispatch to SFA` = pharmacy_dispatch,
                `Pharmacy Stock` = pharmacy_stock,
                `Pharmacy Returns (Unused) from SFA` = pharmacy_unused_return,
                `Pharmacy Returns (Unusable / Lost) from SFA` = pharmacy_unusable_return,
                `Pharmacy Returns (Empty Blisters) from SFA` = pharmacy_empty_blister_return
                )


reactable(
  tbl,
  columns = list(
    name = colDef(name = 'Stock Name', minWidth = 200, filterable = TRUE),
    run_date = colDef(name = 'Run Date', minWidth = 100),
    `Pharmacy Returns (Unusable / Lost) from SFA` = colDef(name = 'Pharmacy Returns (Unusable / Lost) from SFA', minWidth = 110)
  ),
  groupBy = "name"
)
```

## SFA to FA Flow Summary
```{r}
tbl <- df %>% 
  dplyr::mutate(sfa_stock = (sfa_arrival - sfa_dispatch) + sfa_unused_return) %>%
  dplyr::select(run_date, 
                name,
                `SFA Arrival` = sfa_arrival,
                `SFA Dispatch to FA` = sfa_dispatch,
                `SFA Stock` = sfa_stock,
                `SFA Returns (Unused) from FA` = sfa_unused_return,
                `SFA Returns (Unusable / Lost) from FA` = sfa_unusable_return,
                `SFA Returns (Empty Blisters) from FA` = sfa_empty_blister_return
                )


reactable(
  tbl,
  columns = list(
    name = colDef(name = 'Stock Name', minWidth = 200, filterable = TRUE),
    run_date = colDef(name = 'Run Date', minWidth = 100),
    `SFA Returns (Unusable / Lost) from FA` = colDef(name = 'SFA Returns (Unusable / Lost) from FA', minWidth = 110)
  ),
  groupBy = "name"
)
```


## FA to CL Flow Summary
```{r}
tbl <- df %>% 
  dplyr::mutate(fa_stock = fa_arrival - (fa_dispatch + fa_unused_return)) %>%
  dplyr::select(run_date, 
                name,
                `FA Arrival` = fa_arrival,
                `FA Dispatch to CLs` = fa_dispatch,
                `FA Stock` = fa_stock,
                `FA Returns (Unused) from CLs` = fa_unused_return,
                `FA Returns (Unusable / Lost) from CLs` = fa_unusable_return,
                `FA Returns (Empty Blisters) from CLs` = fa_empty_blister_return,
                `Stock Used by CLs` = stock_used_by_cl
                )


reactable(
  tbl,
  columns = list(
    name = colDef(name = 'Stock Name', minWidth = 200, filterable = TRUE),
    run_date = colDef(name = 'Run Date', minWidth = 100),
    `FA Returns (Unusable / Lost) from CLs` = colDef(name = 'FA Returns (Unusable / Lost) from CLs', minWidth = 110)
  ),
  groupBy = "name"
)
```


```{r}
data_list <- list()
col_list <- c('run_date',
              'instanceID', 
              'SubmissionDate',
              'current_weight',
              'visit',
              'cluster', 
              'wid', 
              'hhid', 
              'extid', 
              'source')


data_list$safety <- safety_hist %>% 
    dplyr::filter(participant_take_drug == 'yes', num_ivermectin_tablets_taken>0) %>% 
    tidyr::drop_na(num_tablets_per_weight) %>%
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      visit,
      cluster, 
      wid, 
      hhid, 
      extid, 
      num_tablets_per_weight,
      num_tablets_per_weight_2, 
      num_ivermectin_tablets_taken, 
      num_ivermectin_tablets_taken_2,
      num_albendzole_pills,
      num_albendzole_pills_2,
      current_weight) %>% 
    dplyr::mutate(
      ivm_dose = coalesce(num_tablets_per_weight,
                          num_tablets_per_weight_2),
      ivm_taken = coalesce(num_ivermectin_tablets_taken,
                           num_ivermectin_tablets_taken_2)) %>% 
    dplyr::mutate(alb_taken = coalesce(num_albendzole_pills,
                                       num_albendzole_pills_2),
                  alb_dose = case_when(!is.na(alb_taken)~1, TRUE ~ NA_integer_)) %>%
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      current_weight,
      cluster, 
      visit,
      wid, 
      hhid, 
      extid, 
      ivm_dose,
      ivm_taken, 
      alb_dose,
      alb_taken) %>% 
    dplyr::mutate(source = 'safety') %>% 
    tidyr::pivot_longer(cols = !all_of(col_list)) %>% 
    dplyr::mutate(
      wid = as.character(wid),
      iptype = case_when(stringr::str_detect(name, 'ivm') ~ 'IVM',
                                  stringr::str_detect(name, 'alb') ~ 'ALB',
                                  stringr::str_detect(name, 'coartem') ~ 'coartem',
                                  stringr::str_detect(name, 'prdt') ~ 'pRDT')) %>% 
    tidyr::separate(col = name, into = c('prefix','action'), sep = "_") %>% 
    tidyr::drop_na(value) %>% 
    tidyr::pivot_wider(names_from = action, values_from = value)

data_list$safetynew <- safetynew_hist %>% 
    dplyr::filter(participant_take_drug == 'yes', (num_albendzole_pills>0 | num_ivermectin_tablets_taken>0)) %>% 
    tidyr::drop_na(num_tablets_per_weight) %>%
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      cluster, 
      visit,
      wid, 
      hhid, 
      extid, 
      num_tablets_per_weight,
      num_tablets_per_weight_2, 
      num_ivermectin_tablets_taken, 
      num_ivermectin_tablets_taken_2,
      num_albendzole_pills,
      num_albendzole_pills_2,
      current_weight) %>% 
    dplyr::mutate(ivm_dose = coalesce(num_tablets_per_weight,num_tablets_per_weight_2),
                  ivm_taken = coalesce(num_ivermectin_tablets_taken,num_ivermectin_tablets_taken_2)) %>% 
    dplyr::mutate(alb_taken = coalesce(num_albendzole_pills, num_albendzole_pills_2),
                  alb_dose = 1) %>%
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      current_weight,
      cluster, 
      visit,
      wid, 
      hhid, 
      extid, 
      ivm_dose,
      ivm_taken, 
      alb_dose,
      alb_taken) %>% 
    dplyr::mutate(source = 'safetynew') %>% 
    tidyr::pivot_longer(cols = !all_of(col_list)) %>% 
    dplyr::mutate(
      wid = as.character(wid),
      iptype = case_when(stringr::str_detect(name, 'ivm') ~ 'IVM',
                                  stringr::str_detect(name, 'alb') ~ 'ALB',
                                  stringr::str_detect(name, 'coartem') ~ 'coartem',
                                  stringr::str_detect(name, 'prdt') ~ 'pRDT')) %>% 
    tidyr::separate(col = name, into = c('prefix','action'), sep = "_") %>% 
    tidyr::drop_na(value) %>% 
    tidyr::pivot_wider(names_from = action, values_from = value)


data_list$efficacy <- efficacy_hist %>% 
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      cluster, 
      wid, 
      visit,
      hhid, 
      extid, 
      coartem_taken = num_coartem_tablets_given, 
      current_weight,
      have_80_480_coartem) %>% 
    tidyr::drop_na(coartem_taken) %>%
    dplyr::mutate(
      coartem_dose = case_when(
        current_weight >= 5 & current_weight <= 14.99 ~ 6,
        current_weight >= 15 & current_weight <= 24.99 ~ 12,
        current_weight >= 25 & current_weight <= 34.99 ~ 18,
        current_weight >= 35 & have_80_480_coartem == 'yes' ~ 6,
        current_weight >= 35 & have_80_480_coartem == 'no' ~ 24)
    ) %>%
    dplyr::select(
      run_date,
      instanceID, 
      SubmissionDate,
      current_weight,
      cluster, 
      visit,
      wid, 
      hhid, 
      extid, 
      coartem_dose,
      coartem_taken) %>% 
    dplyr::mutate(source = 'efficacy') %>% 
    tidyr::pivot_longer(cols = !all_of(col_list)) %>% 
    dplyr::mutate(
      wid = as.character(wid),
      iptype = case_when(stringr::str_detect(name, 'ivm') ~ 'IVM',
                                  stringr::str_detect(name, 'alb') ~ 'ALB',
                                  stringr::str_detect(name, 'coartem') ~ 'coartem',
                                  stringr::str_detect(name, 'prdt') ~ 'pRDT')) %>% 
    tidyr::separate(col = name, into = c('prefix','action'), sep = "_") %>% 
    tidyr::drop_na(value) %>% 
    tidyr::pivot_wider(names_from = action, values_from = value)


df <- data_list %>% 
    purrr::reduce(dplyr::bind_rows) %>%
    dplyr::select(
      run_date,
      instanceID,
      wid,
      SubmissionDate,
      weight = current_weight, 
      visit, 
      study = source, 
      cluster, 
      iptype, 
      extid, 
      taken, 
      dose) %>% 
    dplyr::mutate(overdose = case_when(taken > dose ~ 1, TRUE ~ 0),
                  underdose = case_when(taken < dose ~ 1, TRUE ~ 0)) %>% 
    dplyr::inner_join(assignments, by = c("cluster" = "cluster_number")) 
```


## Overdosing/Underdosing Summary
```{r}
tbl <- df %>% 
    dplyr::filter(run_date >= MIN_DATE) %>% 
    dplyr::group_by(iptype, run_date) %>% 
    dplyr::summarise(`Individual Overdose` = n_distinct(extid[overdose==1]),
                     `Individual Underdose` = n_distinct(extid[underdose==1]))

reactable(tbl, groupBy = c('iptype'))
```



## Overdosing Review
```{r}
curr_week <- floor_date(lubridate::today(), 'week')

element_id <- 'pharmacy_overdosing'
tbl <- reactable(df %>% 
            dplyr::filter(overdose == 1) %>% 
            dplyr::filter(run_date == max(.$run_date)) %>% 
            dplyr::select(-underdose, -overdose, -location) %>%
            dplyr::select(wid, assignment, everything()),
            columns = list(
                `SubmissionDate` = colDef(name = 'SubmissionDate', minWidth = 200)
            ),
            highlight = TRUE,
            resizable = TRUE,
            bordered = TRUE,
            striped = TRUE,
            wrap = TRUE,
            filterable=TRUE,
            elementId = element_id,
            groupBy = c("iptype", "visit")
)

wrap_download(tbl, 
              element_id, 
              'pharmacy_overdosing.csv')
```

## Underdosing Review
```{r}
element_id <- 'pharmacy_underdosing'
tbl <- reactable(df %>% 
            dplyr::filter(underdose == 1) %>% 
            dplyr::filter(run_date == max(.$run_date)) %>% 
            dplyr::select(-underdose, -overdose, -location) %>%
            dplyr::select(wid, assignment, everything()),
            columns = list(
                `SubmissionDate` = colDef(name = 'SubmissionDate', minWidth = 200)
            ),
            highlight = TRUE,
            resizable = TRUE,
            bordered = TRUE,
            striped = TRUE,
            wrap = TRUE,
            filterable=TRUE,
            elementId = element_id,
            groupBy = c("iptype", "visit")
)

wrap_download(tbl, 
              element_id, 
              'pharmacy_underdosing.csv')
```
